\documentclass[11pt,letterpaper]{article}
\pagestyle{empty}
\parskip .5ex
\textwidth 7.in
\textheight 9.0in
\oddsidemargin 0in
\evensidemargin 0in
\topmargin -1in
\renewcommand{\baselinestretch}{1.2}
\begin{document}
\centerline{\underline{\textbf{Curriculum Vitae}}}
\noindent Notarization.   I have read the following and certify that this \textit{curriculum vitae} is a current and accurate statement of my professional record.


Signature\ \line(1,0){250}\ Date\ \line(1,0){150}

\begin{itemize}\itemsep0em
\item \textbf{Please organize your CV using the headings and sub-headings in this template.}
\item \textbf{In general, do not list a work or activity more than once.}
\item \textbf{Certain sections with numerous sub-categories include a special sub-category for historical data in which you can group, for convenience, all items from 10+ years ago.}
\end{itemize}
\textbf{I. Personal Information}


\underline{I.A. UID, Last Name, First Name, Middle Name, Contact Information}

\textit{Include mailing address, email, URL}


\underline{I.B. Academic Appointments at UMD}

\textit{Include specific dates}


\underline{I.C. Administrative Appointments at UMD}

\textit{Include specific dates}


\underline{I.D. Other Employment}

\textit{Include specific dates}


\underline{I.E. Educational Background}

\textit{Include dates, degrees, and institutions}


\underline{I.F. Professional Certifications and Licenses}


\textbf{II. Research, Scholarly and Creative Activities}

\textit{For each of the categories listed below follow these guidelines:}

\begin{itemize}\itemsep0em
\item \textit{List published works first, in either chronological order or its inverse, followed (or preceded) by works not yet published but accepted for publication.}
\item \textit{If pre-print electronic publication (epub) exists, indicate and include URL and anticipated date of print publication.}
\item \textit{Submitted works under review or in progress should be listed in section II.L.}
\item \textit{Include page numbers as part of a complete citation for publications.}
\item \textit{Use the appropriate sub-headings for authored vs. edited works and between refereed vs. non-refereed outlets.}
\item \textit{All authors should be listed in the order they appear on the publication.}
\item \textit{When the work is a product of a large group (more than 10 authors), not all authors need be listed.  As an example, the first three, the last three, and the individual him/herself (including his/her place in the total author list) may be listed.}
\end{itemize}

\noindent\underline{II.A. Books \textit{(include full citation information and ISBN)}}

II.A.1. Books Authored \textit{(specify original or revised edition)}

II.A.2. Books Edited

II.A.3. Books Translated \textit{(as translator)}

II.A.4. Textbooks

II.A.5. Major Reference Works

II.A.6. Exhibition Catalogs

II.A.7. Other


\underline{II.B. Chapters}

II.B.1. Books

II.B.2. Collections

II.B.3. Encyclopedia

II.B.4. Series

II.B.5. Research Paper

II.B.6. Other


\underline{II.C. Articles in Refereed Journals}

\textit{Full citation, inclusive of all authors in the order of publication and page numbers. Review articles and invited articles should be so identified. Optional: include DOI.}

II.D. Published Conference Proceedings

II.D.1. Refereed Conference Proceedings

II.D.2. Non-Refereed Conference Proceedings

II.D.3. Historical Conference Proceedings (10+ years ago)

II.D.4. Other


\underline{II.E. Conferences, Workshops, and Talks}

II.E.1. Keynotes

II.E.2. Invited Talks

II.E.3. Refereed Presentations

II.E.4. Refereed Abstracts

II.E.5. Refereed Posters

II.E.6. Refereed Panels

II.E.7. Non-Refereed Presentations

II.E.8. Non-Refereed Abstracts

II.E.9. Non-Refereed Posters

II.E.10. Non-Refereed Panels

II.E.11. Symposia

II.E.12. Workshops

II.E.13. Colloquia

II.E.14. Historical Conferences, Workshops, Talks (10+ years ago)

II.E.15. Other


\underline{II.F. Professional Publications}

II.F.1. Reports and Non-Refereed Monographs

II.F.2. Pre-Print/Working Paper (Not Work in Progress)

II.F.3. Legal Briefs

II.F.4. Policy Briefs

II.F.5. Other


\underline{II.G. Book Reviews, Notes, and Other Contributions}

II.G. 1. Book Reviews

II.G. 2. Essays

II.G. 3. Notes

II.G. 4. Manuals

II.G. 5.Other


\underline{II.H. Completed Creative Works}

II.H.1. Digital Media (e.g., CDs, DVDs)

II.H.2. Datasets

II.H.3. Constructed Projects

II.H.4. Demonstrations

II.H.5. Inventions

II.H.6. Original Plans and Designs

II.H.7. Photography

II.H.8. Software and Applications

II.H.9. Websites

II.H.10. Exhibitions and Installations

II.H.11. Curatorial Practice

II.H.12. Performance or Interpretation --- Performing Arts

II.H.13. Direction - Performing Arts

II.H.14. Production - Performing Arts

II.H.15. Costume, Stage, Multimedia, and Theatrical Design

II.H.16. Artistic and Graphic Design

II.H.17. Dramaturgy

II.H.18. Artwork

II.H.19. Choreography

II.H.20. Playwriting, Screenwriting, and Musical Composition

II.H.21. Works of Creative Writing

II.H.22. Performance or Interpretation - Film, Video, and Multimedia

II.H.23. Direction - Film, Video, and Multimedia

II.H.24. Production - Film, Video, and Multimedia

II.H.25. Citations and Reviews

II.H.26. Historical Completed Creative Works (10+ years ago)

II.H.27. Other


\underline{II.I Significant Works in Public Media}

\textit{Specify the following --- Title, Publication/Media Name, Contributors, Types (Print, online, broadcast, video, documentary)}

II.I.1. Explanatory, Investigative, or Long-Form Journalism

II.I.2. Other Significant Journalism

II.I.3. Commentary/Analysis

II.I.4. Interactive Online Database

II.I.5. Other


\underline{II.J. Sponsored Research}

\textit{List source, title, amount awarded, time period and role (i.e. principal investigator or co-investigator) in reverse chronological order or its inverse.  If there are co-investigators, please list these.}

II.J.1. Grants

II.J.2. Contracts

II.J.3. Other


\underline{II.K. Fellowships, Gifts and Other Funded Research}

II.K.1. Fellowships

II.K.2. Gifts

II.K.3. Other


\underline{II.L. Submissions and Works in Progress}

\textit{List press, journal, or granting agency.}

II.L.1. Current Grant Applications

II.L.2. Manuscripts in Preparation

II.L.3. Manuscripts under Review \textit{(indicate status:  submitted or revising to resubmit)}

II.L.4. Working Papers in Preparation

II.L.5. Designs in Preparation

II.L.6. Other


\underline{II.M. Centers for Research, Scholarship, and Creative Activities}

\textit{Specify Name of the Center, Description of Center, Collaborators, Start and End Dates.}

II.M.1. Centers Established

II.M.2. Centers Directed

II.M.3. Symposia Organized (through center)

II.M.4. Other


\underline{II.N. Patents}

II.N.1. Device

II.N.2. Other


\underline{II.O. Other Research/Scholarship/Creative Activities}


\textbf{III. Teaching, Mentoring and Advising.}


\underline{III.A. Courses Taught}

\textit{Include courses taught in the last five years. Indicate approximate enrollments and any unusual formats.}

\underline{III.B. Teaching Innovations}

III.B.1. Major Programs Established

III.B.2. Education Abroad Established
 
III.B.3. Software, Applications, Online Education, etc.

III.B.4. Instructional Workshops and Seminars Established

III.B.5. Course or Curriculum Development

III.B.6. Historical Innovations (10+ years ago)

III.B.7. Other


\underline{III.C. Advising}: Research or Clinical

\textit{This refers to students whose projects the faculty has supervised as adviser, committee chair, or committee member (indicate role). The name of student, academic year(s) involved, and the name of institution if other than UMD should be indicated, as well as placement of the student(s), if the project is completed.  List completed work first.}

III.C.1. Undergraduate

III.C.2. Master's

III.C.3. Doctoral

III.C.4. Post-doctoral

III.C.5. Other Research Directions (K-12 Interactions)


\underline{III.D. Mentorship}

III.D.1. Junior Faculty

III.D.2. Other


\underline{III.E. Advising: Other than Research Direction}

III.E.1. Undergraduate

III.E.2. Master's

III.E.3. Doctoral

III.E.4. Post-doctoral

III.E.5. Other Advising Activities

\textit{(Include advising student groups, special assignments, recruiting, etc.)}


\underline{III.F. Professional and Extension Education}

III.F.1. Professional Programs Established

III.F.2. Major Extension Programs

III.F.3. Workshops

III.F.4. Other


\underline{III.G. Other Teaching Activities}


\textbf{IV. Service and Outreach}


\underline{IV.A. Editorships, Editorial Boards, and Reviewing Activities}

\textit{Include participation for journals and other learned publications (print and electronic).}

IV.A.1. Editorships

IV.A.2. Editorial Boards

IV.A.3. Reviewing Activities for Journals and Presses

IV.A.4. Reviewing Activities for Agencies and Foundations

IV.A.5. Reviewing Activities for Conferences

IV.A.6. Historical Editorships, etc. (10+ years ago)

IV.A.7. Other


\underline{IV.B. Committees, Professional \& Campus Service}

IV.B.1. Campus Service - Department

IV.B.2. Campus Service - College

IV.B.3. Campus Service - University

IV.B.4. Campus Service - Special Administrative Assignment

IV.B.5. Campus Service - Other

IV.B.6. Offices and Committee Memberships 

IV.B.7. Leadership Roles in Meetings and Conferences

IV.B.8. Other Non-University Committees, Memberships, Panels, etc.

IV.B.9. Historical Committees, etc. (10+ years ago)

IV.B.10. Other


\underline{IV.C. External Service and Consulting}

IV.C.1. Community Engagements, Local, State, National, International

IV.C.2. International Activities 

IV.C.3. Corporate and Other Board Memberships

IV.C.4. Entrepreneurial Activities

IV.C.5. Consultancies (to local, state and federal agencies; companies; organizations)

IV.C.6. Historical External Service and Consulting (10+ years ago)

IV.C.7. Other


\underline{IV.D. Non-Research Presentations}

IV.D.1. Outreach Presentations

IV.D.2 Other


\underline{IV.E. Media Contributions}

IV.E.1. Internet

IV.E.2. TV

IV.E.3. Radio

IV.E.4. Digital Media

IV.E.5. Print Media 

IV.E.6. Blogs

IV.E.7. Feeds

IV.E.8. Other


\underline{IV.F Community \& Other Service}


\textbf{V. Awards, Honors and Recognition}

V.1. Research Fellowships, Prizes and Awards

V.2 Teaching Awards

V.3 Service Awards and Honors

V.4 Recognition in Media 

V.5 Other Special Recognition


\textbf{VI. Other Information}





\end{document}
