% the template is called maryland.tex and PJT modified and commented a variety of things to make it nicely
% work in a ADS workflow
% hint: use a custum format, I used :      \\item %\5.1L. %Y, "%\T", %\J, %\({\\bf )V\(} ), %p-%P. [{\\bf %c cit.}] %% %W
%       see README file for more detailed instructions
% Empty records have been %%-commented out to keep the PDF from having too much whitespace.

\documentclass[11pt,letterpaper]{article}
\usepackage{enumitem}   % PJT
\pagestyle{empty}
\parskip .5ex
\textwidth 7.in
\textheight 9.0in
\oddsidemargin 0in
\evensidemargin 0in
\topmargin -1in
\renewcommand{\baselinestretch}{1.2}

% PJT
\newcommand{\newi}{\newline\indent}
\newcommand{\newl}{\newline}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2.5mm}
% PJT - some ADS abbreviations they use
\newcommand{\amp}{\&}
\newcommand{\ap}{$\sim$}
\newcommand{\rsquo}{'}
% \setcounter{enumi}{1000}      % not needed?

\begin{document}

\centerline{\underline{\textbf{Curriculum Vitae}}}
\noindent Notarization.   I have read the following and certify that this \textit{curriculum vitae} is a current and accurate statement of my professional record.

\bigskip\bigskip
Signature\ \line(1,0){250}\ Date\ \line(1,0){150}

% \begin{itemize}\itemsep0em
% \item \textbf{Please organize your CV using the headings and sub-headings in this template.}
% \item \textbf{In general, do not list a work or activity more than once.}
% \item \textbf{Certain sections with numerous sub-categories include a special sub-category for historical data in which you can group, for convenience, all items from 10+ years ago.}
% \end{itemize}

\bigskip\bigskip

\textbf{I. Personal Information}


\underline{I.A. UID, Last Name, First Name, Middle Name, Contact Information}

% \textit{Include mailing address, email, URL}
UID: 01690780\newi
Peter J. Teuben\newi
Astronomy Department\newi
University of Maryland\newi
College Park, MD 20742\newi
{\tt teuben@astro.umd.edu}\newi
{\tt http://www.astro.umd.edu/$\sim$teuben}\newi


\underline{I.B. Academic Appointments at UMD}

% \textit{Include specific dates}
%  using ~ to fight the kerning and avoiding to use a \table
2010-~~~~~~~~	Associate Research Scientist\newi
2001-2010~~	Assistant Research Scientist\newi
1989-2001~~	Postdoctoral Fellow / Research Associate\newi


\underline{I.C. Administrative Appointments at UMD}

% \textit{Include specific dates}


\underline{I.D. Other Employment}

% \textit{Include specific dates}
1987-1989~~~~	Postdoctoral Fellow, University of Illinois,Urbana-Champaign, IL\newi
1986-1987~~~~	Member, Institute for Advanced Study, Princeton, NJ\newi


\underline{I.E. Educational Background}

% \textit{Include dates, degrees, and institutions}

1986~~~~	Ph.D., University of Groningen, Netherlands\newi
1981~~~~	M.S. (equiv), University of Groningen, Netherlands\newi
1979~~~~	B.S.(equiv), University of Groningen, Netherlands\newi

\underline{I.F. Professional Certifications and Licenses}


\textbf{II. Research, Scholarly and Creative Activities}

% \textit{For each of the categories listed below follow these guidelines:}
% 
% \begin{itemize}\itemsep0em
% \item \textit{List published works first, in either chronological order or its inverse, followed (or preceded) by works not yet published but accepted for publication.}
% \item \textit{If pre-print electronic publication (epub) exists, indicate and include URL and anticipated date of print publication.}
% \item \textit{Submitted works under review or in progress should be listed in section II.L.}
% \item \textit{Include page numbers as part of a complete citation for publications.}
% \item \textit{Use the appropriate sub-headings for authored vs. edited works and between refereed vs. non-refereed outlets.}
% \item \textit{All authors should be listed in the order they appear on the publication.}
% \item \textit{When the work is a product of a large group (more than 10 authors), not all authors need be listed.  As an example, the first three, the last three, and the individual him/herself (including his/her place in the total author list) may be listed.}
% \end{itemize}

\noindent\underline{II.A. Books \textit{(include full citation information and ISBN)}}

%% II.A.1. Books Authored \textit{(specify original or revised edition)}

II.A.2. Books Edited

\begin{itemize}


% 17 PROCEEDINGS  
\item[] 
Blitz, L.~and Teuben, P.~J.\  1996,  ``Unsolved problems of the Milky Way: 
proceedings of the 169th Symposium of the International Astronomical Union, 
held in The Hague, The Netherlands, August 23-29, 1994''., Unsolved Problems 
of the Milky Way,  {\bf 169} ,  [{\bf 16 cit.}] ISBN-13: 978-0792340409

% ISBN-13: 978-0792340409
% ISBN-10: 079234040X

\end{itemize}


%% II.A.3. Books Translated \textit{(as translator)}

%% II.A.4. Textbooks

%% II.A.5. Major Reference Works

%% II.A.6. Exhibition Catalogs

%% II.A.7. Other


\underline{II.B. Chapters}

II.B.1. Books

\begin{itemize}
\item[]
Blitz, Leo, Spergel, David N., Teuben, Peter J., and Hartmann, Dap.  2004,  
``High-Velocity Clouds: the Missing Link?'', High Velocity Clouds,  312,  
297-312 [0 cit.] ISBN 1-4020-2578-5
\end{itemize}
% ISBN 1-4020-2578-5

%% II.B.2. Collections

%% II.B.3. Encyclopedia

%% II.B.4. Series

%% II.B.5. Research Paper

%% II.B.6. Other


\underline{II.C. Articles in Refereed Journals}

%\textit{Full citation, inclusive of all authors in the order of publication and page numbers. Review articles and invited articles should be so identified. Optional: include DOI.}

II.C.1. Refereed Journal Articles

% PJT-ADS-1
\setcounter{enumi}{1}   % TEST
\begin{enumerate}[label=\textbf{\arabic*}.]

% 2 ARTICLE  
\item  
Teuben, P.~J.~and Sanders, R.~H.\ 1985,  ``Dynamical rules for barred 
spiral galaxies'', Monthly Notices of the Royal Astronomical Society,  {\bf 
212} , 257-273.\  [{\bf 76 cit.}] 
  
% 3 ARTICLE  
\item  
Teuben, P., Turner, E.~L., and Schwarzschild, M.\  1985,  "An analysis of 
observations of the streaming velocities in the bulge of M31", The 
Astrophysical Journal,  {\bf 289} , 58-66.  [{\bf 4 cit.}] 

% 4 ARTICLE  
% \item  
% Teuben, P.~J.~and Sanders, R.~H..\  1985,  "Erratum - Dynamical Rules for 
% Barred Spiral Galaxies", Monthly Notices of the Royal Astronomical Society,  
% {\bf 214} , 319- [{\bf 2 cit.}] 

% 5 ARTICLE  
\item  
Teuben, P.~J., Sanders, R.~H., Atherton, P.~D., and van Albada, G.~D.\  
1986,  "Kinematics and dynamics of the central region in the barred galaxy 
NGC 1365", Monthly Notices of the Royal Astronomical Society,  {\bf 221} , 
1-13.  [{\bf 52 cit.}] 

% 6 ARTICLE  
\item  
Teuben, P.\  1987,  "Self-consistent equilibrium models for the perfect 
elliptic disc", Monthly Notices of the Royal Astronomical Society,  {\bf 
227} , 815-841.  [{\bf 18 cit.}] 

% 7 ARTICLE  
\item  
Skillman, E.~D., Terlevich, R., Teuben, P.~J., and van Woerden, H.\  1988,  
"H I synthesis observations of the dwarf irregular galaxy Sextans A", 
Astronomy and Astrophysics (ISSN 0004-6361), vol.~198, no.~1-2, June 1988, 
p.~33-42.,  {\bf 198} , 33-42.  [{\bf 101 cit.}] 

% 8 ARTICLE  
\item  
Phookun, B., Mundy, L.~G., Teuben, P.~J., and Wainscoat, R.~J.\  1992,  
"NGC 4027 - an interacting one-armed spiral galaxy with a warped ring", The 
Astrophysical Journal,  {\bf 400} , 516-527.  [{\bf 25 cit.}] 

% 9 ARTICLE  
\item  
Vogel, S.~N., Rand, R.~J., Gruendl, R.~A., and Teuben, P.~J.\  1993,  
"H-alpha Fabry-Perot observations of the density-wave pattern in M51", 
Publications of the Astronomical Society of the Pacific,  {\bf 105} , 
666-669.  [{\bf 36 cit.}] 


% 11 ARTICLE   PJT-MOVE
% \item  
% Blitz, L.~and Teuben, P..\  1995,  "Symposium 169: Unresolved Problems of 
% the Milky Way", Comments on Astrophysics,  {\bf 18} , 51- [{\bf 0 cit.}] 

% 12 ARTICLE  
\item  
Piner, B.~G., Stone, J.~M., and Teuben, P.~J.\  1995,  "Nuclear Rings and 
Mass Inflow in Hydrodynamic Simulations of Barred Galaxies", The 
Astrophysical Journal,  {\bf 449} , 508- [{\bf 165 cit.}] 

% 13 ARTICLE  
\item  
Regan, M.~W., Vogel, S.~N., and Teuben, P.~J.\  1995,  "Dust and Molecular 
Gas in the Barred Spiral Galaxy NGC 1530", The Astrophysical Journal,  {\bf 
449} , 576- [{\bf 32 cit.}] 

% 14 INPROCEEDINGS   PJT-MOVE
% \item  
% Teuben, P., Regan, M., and Vogel, S..\  1996,  "The Barred Galaxy NGC 
% 1530", Lecture Notes in Physics, Berlin Springer Verlag,  {\bf 474} , 125- 
% [{\bf 0 cit.}] 

% 15 ARTICLE  
\item  
Welch, W.~J., and 36 colleagues.\  1996,  "The 
Berkeley-Illinois-Maryland-Association Millimeter Array", Publications of 
the Astronomical Society of the Pacific,  {\bf 108} , 93- [{\bf 141 cit.}] 

% 17 ARTICLE  
\item  
Regan, M.~W., Teuben, P.~J., Vogel, S.~N., and van der Hulst, T.\  1996,  
"The Morphology of the Stars, Atomic Gas, and Ionized Gas in the Barred 
Spiral Galaxy NGC 1530", The Astronomical Journal,  {\bf 112} , 2549- [{\bf 
33 cit.}] 

% 18 ARTICLE  
\item  
Regan, M.~W., Vogel, S.~N., and Teuben, P.~J.\  1997,  "The Mass Inflow 
Rate in the Barred Galaxy NGC 1530", The Astrophysical Journal,  {\bf 482} 
, L143-L147.  [{\bf 86 cit.}] 


% 20 ARTICLE  
\item  
Barsony, M., Kenyon, S.~J., Lada, E.~A., and Teuben, P.~J.\  1997,  "A 
Near-Infrared Imaging Survey of the {$\rho$} Ophiuchi Cloud Core", The 
Astrophysical Journal Supplement Series,  {\bf 112} , 109-191.  [{\bf 118 
cit.}] 

% 21 ARTICLE  
\item  
Falcke, H., and 5 colleagues.\  1998,  "The Simultaneous Spectrum of 
Sagittarius A* from 20 Centimeters to 1 Millimeter and the Nature of the 
Millimeter Excess", The Astrophysical Journal,  {\bf 499} , 731-734.  [{\bf 
147 cit.}] 


% 23 ARTICLE  
\item  
Blitz, L., Spergel, D.~N., Teuben, P.~J., Hartmann, D., and Burton, W.~B.\  
1999,  "High-Velocity Clouds: Building Blocks of the Local Group", The 
Astrophysical Journal,  {\bf 514} , 818-843.  [{\bf 382 cit.}] 

% 24 ARTICLE  
\item  
Sheth, K., Regan, M.~W., Vogel, S.~N., and Teuben, P.~J.\  2000,  
"Molecular Gas, Dust, and Star Formation in the Barred Spiral NGC 5383", 
The Astrophysical Journal,  {\bf 532} , 221-237.  [{\bf 78 cit.}] 

% 25 ARTICLE  
\item  
Hanisch, R.~J., and 7 colleagues.\  2001,  "Definition of the Flexible 
Image Transport System (FITS)", Astronomy and Astrophysics, v.376, 
p.359-380 (2001),  {\bf 376} , 359-380.  [{\bf 97 cit.}] 

% 26 ARTICLE  
\item  
Maciejewski, W., Teuben, P.~J., Sparke, L.~S., and Stone, J.~M.\  2002,  
"Gas inflow in barred galaxies - effects of secondary bars", Monthly 
Notices of the Royal Astronomical Society,  {\bf 329} , 502-512.  [{\bf 104 
cit.}] 

% 27 ARTICLE  
\item  
Helfer, T.~T., Vogel, S.~N., Lugten, J.~B., and Teuben, P.~J.\  2002,  
"Imaging Simulations of Large-Scale Flux Recovery at Millimeter 
Wavelengths", Publications of the Astronomical Society of the Pacific,  
{\bf 114} , 350-371.  [{\bf 19 cit.}] 

% 28 ARTICLE  
\item  
Regan, M.~W., Sheth, K., Teuben, P.~J., and Vogel, S.~N.\  2002,  "Inner 
Molecular Rings in Barred Galaxies: BIMA Survey of Nearby Galaxies CO 
Observations", The Astrophysical Journal,  {\bf 574} , 126-133.  [{\bf 22 
cit.}] 

% 29 ARTICLE  
\item  
Sheth, K., and 5 colleagues.\  2002,  "Molecular Gas and Star Formation in 
Bars of Nearby Spiral Galaxies", The Astronomical Journal,  {\bf 124} , 
2581-2599.  [{\bf 90 cit.}] 

% 30 ARTICLE  
\item  
Das, M., and 6 colleagues.\  2003,  "Central Mass Concentration and Bar 
Dissolution in Nearby Spiral Galaxies", The Astrophysical Journal,  {\bf 
582} , 190-195.  [{\bf 30 cit.}] 

% 31 ARTICLE  
\item  
Regan, M.~W.~and Teuben, P.\  2003,  "The Formation of Nuclear Rings in 
Barred Spiral Galaxies", The Astrophysical Journal,  {\bf 582} , 723-742.  
[{\bf 67 cit.}] 

% 32 ARTICLE  
\item  
Hut, P., and 9 colleagues.\  2003,  "MODEST-1: Integrating stellar 
evolution and stellar dynamics", New Astronomy,  {\bf 8} , 337-370.  [{\bf 
38 cit.}] 

% 33 ARTICLE  
\item  
Regan, M.~W.~and Teuben, P.~J.\  2004,  "Bar-driven Mass Inflow: How Bar 
Characteristics Affect the Inflow", The Astrophysical Journal,  {\bf 600} , 
595-612.  [{\bf 76 cit.}] 

% 34 ARTICLE  
\item  
Makarov, V.~V., Olling, R.~P., and Teuben, P.~J.\  2004,  "Kinematics of 
stellar associations: the epicycle approximation and the convergent point 
method", Monthly Notices of the Royal Astronomical Society,  {\bf 352} , 
1199-1207.  [{\bf 19 cit.}] 


% 36 ARTICLE  
\item  
Sheth, K., Vogel, S.~N., Regan, M.~W., Thornley, M.~D., and Teuben, P.~J.\  
2005,  "Secular Evolution via Bar-driven Gas Inflow: Results from BIMA 
SONG", The Astrophysical Journal,  {\bf 632} , 217-226.  [{\bf 160 cit.}]

% 35 ARTICLE  
\item  
Young, K.~E., and 22 colleagues.\  2005,  "The Spitzer c2d Survey of Large, 
Nearby, Interstellar Clouds. I. Chamaeleon II Observed with MIPS", The 
Astrophysical Journal,  {\bf 628} , 283-297.  [{\bf 49 cit.}] 


% 37 ARTICLE  
\item  
Bourke, T.~L., and 14 colleagues.\  2006,  "The Spitzer c2d Survey of 
Nearby Dense Cores. II. Discovery of a Low-Luminosity Object in the 
``Evolved Starless Core'' L1521F", The Astrophysical Journal,  {\bf 649} , 
L37-L40.  [{\bf 118 cit.}] 

% 38 ARTICLE  
\item  
Dunham, M.~M., and 11 colleagues.\  2006,  "The Spitzer c2d Survey of 
Nearby Dense Cores. I. First Direct Detection of the Embedded Source in 
IRAM 04191+1522", The Astrophysical Journal,  {\bf 651} , 945-959.  [{\bf 
77 cit.}] 

% 39 ARTICLE  
\item  
Brooke, T.~Y., and 24 colleagues.\  2007,  "The Spitzer c2d Survey of 
Nearby Dense Cores. IV. Revealing the Embedded Cluster in B59", The 
Astrophysical Journal,  {\bf 655} , 364-374.  [{\bf 49 cit.}] 

% 40 ARTICLE  
\item  
Porras, A., and 21 colleagues.\  2007,  "The Spitzer c2d Survey of Large, 
Nearby, Interstellar Clouds. V. Chamaeleon II Observed with IRAC", The 
Astrophysical Journal,  {\bf 656} , 493-504.  [{\bf 37 cit.}] 

% 41 ARTICLE  
\item  
Shetty, R., Vogel, S.~N., Ostriker, E.~C., and Teuben, P.~J.\  2007,  
"Kinematics of Spiral-Arm Streaming in M51", The Astrophysical Journal,  
{\bf 665} , 1138-1158.  [{\bf 70 cit.}] 

% 42 ARTICLE  
\item  
Chapman, N.~L., and 24 colleagues.\  2007,  "The Spitzer c2d Survey of 
Large, Nearby, Interstellar Clouds. IV. Lupus Observed with MIPS", The 
Astrophysical Journal,  {\bf 667} , 288-302.  [{\bf 28 cit.}] 

% 43 ARTICLE   PJT-MOVE
% \item  
% Portegies Zwart, S., and 21 colleagues.\  2008,  "A Multiphysics and 
% Multiscale Software Environment for Modeling Astrophysical Systems", 
% Lecture Notes in Computer Science,  {\bf 5102} , 207-216.  [{\bf 2 cit.}] 

% 44 ARTICLE  
\item  
Padgett, D.~L., and 23 colleagues.\  2008,  "The Spitzer c2d Survey of 
Large, Nearby, Interstellar Clouds. VII. Ophiuchus Observed with MIPS", The 
Astrophysical Journal,  {\bf 672} , 1013-1037- [{\bf 68 cit.}] 

% 45 ARTICLE  
\item  
Stone, J.~M., Gardiner, T.~A., Teuben, P., Hawley, J.~F., and Simon, 
J.~B.\  2008,  "Athena: A New Code for Astrophysical MHD", The 
Astrophysical Journal Supplement Series,  {\bf 178} , 137-177- [{\bf 397 
cit.}] 

% 46 ARTICLE  
\item  
Corder, S., and 15 colleagues.\  2009,  "A Resolved Ring of Debris Dust 
around the Solar Analog HD 107146", The Astrophysical Journal,  {\bf 690} , 
L65-L68.  [{\bf 28 cit.}] 

% 47 ARTICLE  
\item  
Portegies Zwart, S., and 23 colleagues.\  2009,  "A multiphysics and 
multiscale software environment for modeling astrophysical systems", New 
Astronomy,  {\bf 14} , 369-378.  [{\bf 74 cit.}] 

% 48 ARTICLE  
\item  
Koda, J., and 22 colleagues.\  2009,  "Dynamically Driven Evolution of the 
Interstellar Medium in M51", The Astrophysical Journal,  {\bf 700} , 
L132-L136.  [{\bf 98 cit.}] 

% 49 ARTICLE  
\item  
Kunneriath, D., and 30 colleagues.\  2010,  "Coordinated NIR/mm 
observations of flare emission from Sagittarius A*", Astronomy and 
Astrophysics, Volume 517, id.A46, 14 pp.,  {\bf 517} , A46- [{\bf 19 cit.}] 

% 50 ARTICLE  
\item  
P{\'e}rez, L.~M., and 18 colleagues.\  2010,  "Atmospheric Phase Correction 
Using CARMA-PACS: High Angular Resolution Observations of the FU Orionis 
Star PP 13S*", The Astrophysical Journal,  {\bf 724} , 493-501.  [{\bf 21 
cit.}] 

% 51 ARTICLE  
\item  
Koda, J., and 8 colleagues.\  2011,  "CO(J = 1-0) Imaging of M51 with CARMA 
and the Nobeyama 45 m Telescope", The Astrophysical Journal Supplement 
Series,  {\bf 193} , 19- [{\bf 34 cit.}] 

% 52 ARTICLE  
\item  
Enoch, M.~L., and 15 colleagues.\  2011,  "Disk and Envelope Structure in 
Class 0 Protostars. II. High-resolution Millimeter Mapping of the Serpens 
Sample", The Astrophysical Journal Supplement Series,  {\bf 195} , 21- 
[{\bf 42 cit.}] 

% 53 ARTICLE  
\item  
Eckart, A., and 19 colleagues.\  2012,  "Millimeter to X-ray flares from 
Sagittarius A*", Astronomy {\amp} Astrophysics, Volume 537, id.A52, 18 
pp.,  {\bf 537} , A52- [{\bf 39 cit.}] 

% 54 ARTICLE  
\item  
Kunneriath, D., and 12 colleagues.\  2012,  "The Galactic centre 
mini-spiral in the mm-regime", Astronomy {\amp} Astrophysics, Volume 538, 
id.A127, 8 pp.,  {\bf 538} , A127- [{\bf 21 cit.}] 

% 55 ARTICLE  
\item  
Kim, W.-T., Seo, W.-Y., Stone, J.~M., Yoon, D., and Teuben, P.~J.\  2012,  
"Central Regions of Barred Galaxies: Two-dimensional Non-self-gravitating 
Hydrodynamic Simulations", The Astrophysical Journal,  {\bf 747} , 60- 
[{\bf 40 cit.}] 

% 56 ARTICLE  
\item  
Kuzio de Naray, R., and 6 colleagues.\  2012,  "Searching for 
non-axisymmetries in NGC 6503: a weak end-on bar", Monthly Notices of the 
Royal Astronomical Society,  {\bf 427} , 2523-2536.  [{\bf 18 cit.}] 

% 57 ARTICLE  
\item  
Bauermeister, A., and 6 colleagues.\  2013,  "The EGNoG Survey: Gas 
Excitation in Normal Galaxies at z {\ap} 0.3", The Astrophysical Journal,  
{\bf 763} , 64- [{\bf 13 cit.}] 

% 58 ARTICLE  
\item  
Shamir, L., and 8 colleagues.\  2013,  "Practices in source code sharing in 
astrophysics", Astronomy and Computing,  {\bf 1} , 54-58.  [{\bf 6 cit.}] 

% 59 ARTICLE  
\item  
Plambeck, R.~L., and 14 colleagues.\  2013,  "The Ionized Circumstellar 
Envelopes of Orion Source I and the Becklin-Neugebauer Object", The 
Astrophysical Journal,  {\bf 765} , 40- [{\bf 16 cit.}] 

% 60 ARTICLE  
\item  
Bauermeister, A., and 8 colleagues.\  2013,  "The EGNoG Survey: Molecular 
Gas in Intermediate-Redshift Star-Forming Galaxies", The Astrophysical 
Journal,  {\bf 768} , 132- [{\bf 36 cit.}] 

% 61 ARTICLE  
\item  
Katz, H., McGaugh, S., Teuben, P., and Angus, G.~W.\  2013,  "Galaxy 
Cluster Bulk Flows and Collision Velocities in QUMOND", The Astrophysical 
Journal,  {\bf 772} , 10- [{\bf 5 cit.}] 

% 62 ARTICLE  
\item  
Fern{\'a}ndez-L{\'o}pez, M., and 17 colleagues.\  2014,  "CARMA Large Area 
Star Formation Survey: Observational Analysis of Filaments in the Serpens 
South Molecular Cloud", The Astrophysical Journal,  {\bf 790} , L19- [{\bf 
27 cit.}] 

% 63 ARTICLE   PJT-MOVE
% \item  
% Bogert, F.~A., and 14 colleagues.\  2014,  "Computing in Astronomy: 
% Applications and Examples", Computing,  {\bf 47} , 62-69.  [{\bf 0 cit.}] 

% 64 ARTICLE  
\item  
Storm, S., and 24 colleagues.\  2014,  "CARMA Large Area Star Formation 
Survey: Project Overview with Analysis of Dense Gas Structure and 
Kinematics in Barnard 1", The Astrophysical Journal,  {\bf 794} , 165- 
[{\bf 13 cit.}] 

% 65 ARTICLE  
\item  
Lee, K.~I., and 23 colleagues.\  2014,  "CARMA Large Area Star Formation 
Survey: Structure and Kinematics of Dense Gas in Serpens Main", The 
Astrophysical Journal,  {\bf 797} , 76- [{\bf 20 cit.}] 

% 66 ARTICLE  
\item  
Fern{\'a}ndez L{\'o}pez, M., and 7 colleagues.\  2015,  "Panor{\'a}mica del 
proyecto CLASSy", Boletin de la Asociacion Argentina de Astronomia La Plata 
Argentina,  {\bf 57} , 203-205.  [{\bf 0 cit.}] 

% 67 ARTICLE  
\item  
Zauderer, B.~A., and 21 colleagues.\  2016,  "The CARMA Paired Antenna 
Calibration System: Atmospheric Phase Correction for Millimeter Wave 
Interferometry and Its Application to Mapping the Ultraluminous Galaxy Arp 
193", The Astronomical Journal,  {\bf 151} , 18- [{\bf 1 cit.}] 

% 68 ARTICLE  
\item  
Storm, S., and 20 colleagues.\  2016,  "CARMA Large Area Star Formation 
Survey: Dense Gas in the Young L1451 Region of Perseus", The Astrophysical 
Journal,  {\bf 830} , 127- [{\bf 3 cit.}] 

% 69 ARTICLE  
\item  
Bolatto, A.~D., and 23 colleagues.\  2017,  "The EDGE-CALIFA Survey: 
Interferometric Observations of 126 Galaxies with CARMA", The Astrophysical 
Journal,  {\bf 846} , 159- [{\bf 3 cit.}] 


\end{enumerate}


II.C.2  Invited Reviews of Journal Articles


\begin{enumerate}[resume,label=\textbf{\arabic*}.]

% 22 ARTICLE  
\item  
Sheth, K.~and Teuben, P.~J.\  1999,  "Astrophysics:  Stress drives gas 
into a black hole", Nature,  {\bf 397} , 298-299.  [{\bf 3 cit.}] 
** invited for ``news and view'' **

\end{enumerate}

%% II.C.3. Perspectives, Opinions, and Letters

II.C.4. Other


\begin{enumerate}[resume,label=\textbf{\arabic*}.]
  
% 27 ARTICLE  
\item  
Teuben, P.~J.\  1998,  "Computing Like a Professional", Sky and Telescope,  
{\bf 95} ,  [{\bf 0 cit.}] 
** invited article **
  
\end{enumerate}
                

II.D. Published Conference Proceedings

%% II.D.1. Refereed Conference Proceedings

II.D.2. Non-Refereed Conference Proceedings

% PJT-ADS-2

\begin{enumerate}[resume,label=\textbf{\arabic*}.]


% 1 INPROCEEDINGS  
\item  
Teuben, P.~J.~and Sanders, R.~H.\  1983,  "Onset of stochasticity in 
barred spirals", Internal Kinematics and Dynamics of Galaxies,  {\bf 100} , 
211- [{\bf 5 cit.}] 

% 2 INPROCEEDINGS  
\item  
Sanders, R.~H., Teuben, P.~J., and van Albada, G.~D.\  1983,  "Periodic 
Orbits and Gas Flow in Barred Spiral Galaxies", Internal Kinematics and 
Dynamics of Galaxies,  {\bf 100} , 221- [{\bf 13 cit.}] 

% 3 INPROCEEDINGS  
\item  
Teuben, P.\  1987,  "Self-Consistent Elliptical Disks", Structure and 
Dynamics of Elliptical Galaxies,  {\bf 127} , 491- [{\bf 0 cit.}] 


% 5 INBOOK  
\item  
Teuben, P.~and Hut, P.\  1990,  "Head-on collisions between Plummer 
models.", Dynamics and Interactions of Galaxies,  , 227-228.\  [{\bf 0 
cit.}] 

% 6 INPROCEEDINGS  
\item  
Teuben, P.~J.\  1991,  "Velocity Fields of Disks in Triaxial Potentials", 
Warped Disks and Inclined Rings around Galaxies,  , 40- [{\bf 13 cit.}] 





% 13 INPROCEEDINGS  
\item  
Teuben, P.\  1995,  "The Stellar Dynamics Toolbox NEMO", Astronomical Data 
Analysis Software and Systems IV,  {\bf 77} , 398- [{\bf 133 cit.}] 

% 14 INPROCEEDINGS  
\item  
Sault, R.~J., Teuben, P.~J., and Wright, M.~C.~H.\  1995,  "A 
Retrospective View of MIRIAD", Astronomical Data Analysis Software and 
Systems IV,  {\bf 77} , 433- [{\bf 1313 cit.}] 

% 15 INPROCEEDINGS  
\item  
Teuben, P.\  1996,  "Gas and Shocks in Barred Galaxies", IAU Colloq.~157: 
Barred Galaxies,  {\bf 91} , 299- [{\bf 5 cit.}] 

% 16 INPROCEEDINGS  
\item  
Hoffman, W., and 5 colleagues.\  1996,  "Real-Time Observing at Hat Creek", 
Astronomical Data Analysis Software and Systems V,  {\bf 101} , 436- [{\bf 
3 cit.}] 




% 25 INPROCEEDINGS  
\item  
Falcke, H., and 7 colleagues.\  1998,  "SGR A* and Company -- 
Multiwavelength Observations of SGR A* and VLA Search for ``Sgr A*'s'' in 
LINERs", IAU Colloq.~164: Radio Emission from Galactic and Extragalactic 
Compact Sources,  {\bf 144} , 323- [{\bf 0 cit.}] 

% 26 INPROCEEDINGS  
\item  
Teuben, P.~J.\  1998,  "GUI-fying and Documenting your Shell Script", 
Astronomical Data Analysis Software and Systems VII,  {\bf 145} , 116- 
[{\bf 0 cit.}] 





% 30 INPROCEEDINGS  
\item  
Blitz, L., Spergel, D.~N., Teuben, P.~J., and Hartmann, D.\  1999,  "The 
Formation and Evolution of the Milky Way from the Accretion of 
High-Velocity Clouds", The Third Stromlo Symposium: The Galactic Halo,  
{\bf 165} , 480- [{\bf 0 cit.}] 

% 31 INPROCEEDINGS  
\item  
Blitz, L., Spergel, D.~N., Teuben, P.~J., and Hartmann, D.\  1999,  "The 
Formation and Evolution of the Milky Way from the Accretion of 
High-Velocity Clouds", Stromlo Workshop on High-Velocity Clouds,  {\bf 166} 
, 125- [{\bf 2 cit.}] 

% 32 INPROCEEDINGS  
\item  
Teuben, P., Harris, A., Isaak, K., Morgan, J., and Zmuidzinas, J.\  1999,  
"Real-Time Linux Driving a Spectrometer", Astronomical Data Analysis 
Software and Systems VIII,  {\bf 172} , 99- [{\bf 0 cit.}] 

% 33 INPROCEEDINGS  
\item  
Blitz, L., Spergel, D.~N., Teuben, P.~J., and Hartmann, D.\  1999,  "The 
Formation and Evolution of the Milky Way from the Accretion of 
High-Velocity Clouds", The Evolution of Galaxies on Cosmological 
Timescales,  {\bf 187} , 43-56.\  [{\bf 0 cit.}] 

% 34 ARTICLE  
%\item  
%Blitz, L., Spergel, D.~N., Teuben, P.~J., and Hartman, D.\  1999,  "High 
%Velocity Clouds: the Missing Link", ArXiv Astrophysics e-prints,  , 
%arXiv:astro-ph/9901307- [{\bf 1 cit.}] 

% 35 INPROCEEDINGS  
\item  
Pound, M.~W., Wolfire, M.~G., Mundy, L.~G., Teuben, P.~J., and Lord, S.\  
2000,  "DIRT: The Dust InfraRed Toolbox", Astronomical Data Analysis 
Software and Systems IX,  {\bf 216} , 628- [{\bf 3 cit.}] 

% 36 INPROCEEDINGS  
\item  
Teuben, P.~J., Wolfire, M.~G., Pound, M.~W., and Mundy, L.~G.\  2000,  "A 
Commodity Computing Cluster", Astronomical Data Analysis Software and 
Systems IX,  {\bf 216} , 644- [{\bf 0 cit.}] 



% 39 INPROCEEDINGS  
\item  
Teuben, P.~J., and 7 colleagues.\  2001,  "Immersive 4-D Interactive 
Visualization of Large-Scale Simulations", Astronomical Data Analysis 
Software and Systems X,  {\bf 238} , 499- [{\bf 8 cit.}] 

% 40 INPROCEEDINGS  
\item  
Langston, G.~and Teuben, P.\  2001,  "VLA HI Observations of NGC 5713/19", 
Gas and Galaxy Evolution,  {\bf 240} , 862- [{\bf 2 cit.}] 



% 45 INPROCEEDINGS  
\item  
Teuben, P., and 7 colleagues.\  2002,  "Theory in a Virtual Observatory", 
Astronomical Data Analysis Software and Systems XI,  {\bf 281} , 7- [{\bf 5 
cit.}] 


% 49 INPROCEEDINGS  
\item  
Das, M., and 5 colleagues.\  2002,  "Mass Concentration and Bar Dissolution 
in Spiral Galaxies", Disks of Galaxies: Kinematics, Dynamics and 
Peturbations,  {\bf 275} , 157-160.\  [{\bf 1 cit.}] 

% 50 INPROCEEDINGS  
\item  
Teuben, P.~J.\  2002,  "Velocity Fields of Disk Galaxies", Disks of 
Galaxies: Kinematics, Dynamics and Peturbations,  {\bf 275} , 217-228.\  
[{\bf 16 cit.}] 

% 51 INPROCEEDINGS  
\item  
Sheth, K., and 6 colleagues.\  2002,  "Comparing Molecular Gas and Star 
Formation Properties in the Central Regions of Barred and Unbarred 
Spirals", Disks of Galaxies: Kinematics, Dynamics and Peturbations,  {\bf 
275} , 263-266.\  [{\bf 3 cit.}] 

% 52 INPROCEEDINGS  
\item  
Scott, S.~L., and 12 colleagues.\  2003,  "The COBRA/CARMA Correlator Data 
Processing System", Astronomical Data Analysis Software and Systems XII,  
{\bf 295} , 265- [{\bf 4 cit.}] 

% 53 INPROCEEDINGS  
\item  
Plante, R., and 12 colleagues.\  2003,  "CARMA Data Storage, Archiving, 
Pipeline Processing, and the Quest for a Data Format", Astronomical Data 
Analysis Software and Systems XII,  {\bf 295} , 269- [{\bf 27 cit.}] 

% 54 INPROCEEDINGS  
\item  
Johnson, V.~L., Teuben, P.~J., and Penprase, B.~E.\  2003,  "NBodyLab: A 
Testbed for Undergraduates Utilizing a Web Interface to NEMO and MD-GRAPE2 
Hardware", Astronomical Data Analysis Software and Systems XII,  {\bf 295} 
, 365- [{\bf 2 cit.}] 

% 55 INPROCEEDINGS  
\item  
Johnson, V.~L.~and Teuben, P.~J.\  2003,  "Teaching Scientific Computing 
with N-Body Simulations", Astronomical Data Analysis Software and Systems 
XII,  {\bf 295} , 370- [{\bf 0 cit.}] 

% 56 INPROCEEDINGS  
\item  
Pound, M.~W., and 12 colleagues.\  2003,  "CARMA Software Development", 
Astronomical Data Analysis Software and Systems XII,  {\bf 295} , 377- 
[{\bf 1 cit.}] 

% 57 INPROCEEDINGS  
\item  
Teuben, P.\  2003,  "Simulation Software: Then, Now and Virtual 
Observatory", Astrophysical Supercomputing using Particle Simulations,  
{\bf 208} , 359- [{\bf 1 cit.}] 


% 61 INPROCEEDINGS  
\item  
Blitz, L., Spergel, D.~N., Teuben, P.~J., and Hartmann, D.\  2004,  
"High-Velocity Clouds: The Missing Link?", High Velocity Clouds,  {\bf 312} 
, 297- [{\bf 1 cit.}] 

% 62 INPROCEEDINGS  
\item  
Pety, J., and 5 colleagues.\  2004,  "Interoperating GILDAS and MIRIAD", 
Astronomical Data Analysis Software and Systems (ADASS) XIII,  {\bf 314} , 
416- [{\bf 0 cit.}] 

% 63 INPROCEEDINGS  
\item  
Teuben, P.~J.\  2004,  "Genetic Programming and other fitting techniques 
in Galactic Dynamics", Astronomical Data Analysis Software and Systems 
(ADASS) XIII,  {\bf 314} , 621- [{\bf 0 cit.}] 

% 64 INPROCEEDINGS  
\item  
Gwon, C., and 12 colleagues.\  2004,  "The CARMA Control System", 
Astronomical Data Analysis Software and Systems (ADASS) XIII,  {\bf 314} , 
708- [{\bf 1 cit.}] 

% 65 INPROCEEDINGS  
\item  
Amarnath, N.~S., and 12 colleagues.\  2004,  "The CARMA Monitor System 
(CAM) - Transforming Cyclically Collected Telemetry into a Linear Stream", 
Astronomical Data Analysis Software and Systems (ADASS) XIII,  {\bf 314} , 
720- [{\bf 2 cit.}] 

% 66 INPROCEEDINGS  
\item  
Scott, S.~L., and 12 colleagues.\  2004,  "The CARMA Software System", 
Astronomical Data Analysis Software and Systems (ADASS) XIII,  {\bf 314} , 
768- [{\bf 4 cit.}] 

% 67 INPROCEEDINGS  
\item  
Petitpas, G., Das, M., Teuben, P., and Vogel, S.\  2004,  "The Dark Matter 
Content of Barred Spiral Galaxies", Dark Matter in Galaxies,  {\bf 220} , 
277- [{\bf 1 cit.}] 


% 71 INPROCEEDINGS  
\item  
Teuben, P.~J., Stone, J., and Gardiner, T.\  2007,  "Athena: a Grid-Based 
Code for Astrophysical Gas Dynamics", Astronomical Data Analysis Software 
and Systems XVI,  {\bf 376} , 93- [{\bf 0 cit.}] 

% 72 INPROCEEDINGS  
\item  
Thomas, B., Shaya, E., Huang, Z., and Teuben, P.\  2007,  "Knowledge 
Discovery Framework for the Virtual Observatory", Astronomical Data 
Analysis Software and Systems XVI,  {\bf 376} , 563- [{\bf 0 cit.}] 

% 73 INPROCEEDINGS  
\item  
Gheller, C., Becciani, U., and Teuben, P.~J.\  2007,  "Next Generation of 
Visualization Tools for Astrophysics", Astronomical Data Analysis Software 
and Systems XVI,  {\bf 376} , 690- [{\bf 0 cit.}] 

% 74 INPROCEEDINGS  
\item  
Weiner, B., and 15 colleagues.\  2009,  "Astronomical Software Wants To Be 
Free: A Manifesto", astro2010: The Astronomy and Astrophysics Decadal 
Survey,  {\bf 2010} ,  [{\bf 6 cit.}] 


% 76 INPROCEEDINGS  
\item  
P{\'e}rez, L.~M., and 11 colleagues.\  2010,  "Atmospheric phase correction 
using the CARMA paired antennas calibration system", Ground-based and 
Airborne Telescopes III,  {\bf 7733} , 77333T- [{\bf 0 cit.}] 



% 80 ARTICLE  
%\item  
%Koda, J., and 8 colleagues.\  2011,  "CO(1-0) imaging of M51 with CARMA and 
%NRO45", ArXiv e-prints,  , arXiv:1102.3060- [{\bf 0 cit.}] 


% 82 INPROCEEDINGS  
\item  
Kunneriath, D., and 16 colleagues.\  2011,  "The Galactic Centre in the 
Millimeter Regime: Observations with CARMA", The Galactic Center: a Window 
to the Nuclear Environment of Disk Galaxies,  {\bf 439} , 327- [{\bf 2 
cit.}] 


% 84 INPROCEEDINGS  
\item  
Teuben, P.\  2011,  "drPACS: A Simple UNIX Execution Pipeline", 
Astronomical Data Analysis Software and Systems XX,  {\bf 442} , 533- [{\bf 
2 cit.}] 



% 88 INPROCEEDINGS  
\item  
Eckart, A., and 20 colleagues.\  2012,  "Flare emission from Sagittarius 
A*", Journal of Physics Conference Series,  {\bf 372} , 012022- [{\bf 4 
cit.}] 

% 89 INPROCEEDINGS  
\item  
Kunneriath, D., and 12 colleagues.\  2012,  "The Galactic centre 
mini-spiral with CARMA", Journal of Physics Conference Series,  {\bf 372} , 
012063- [{\bf 1 cit.}] 


% 91 INPROCEEDINGS  
\item  
Pound, M.~W.~and Teuben, P.\  2012,  "MIS: A MIRIAD Interferometry 
Singledish Toolkit", Astronomical Data Analysis Software and Systems XXI,  
{\bf 461} , 565- [{\bf 3 cit.}] 

% 92 INPROCEEDINGS  
\item  
Teuben, P., Allen, A., Nemiroff, R.~J., and Shamir, L.\  2012,  "Practices 
in Code Discoverability", Astronomical Data Analysis Software and Systems 
XXI,  {\bf 461} , 623- [{\bf 3 cit.}] 

% 93 INPROCEEDINGS  
\item  
Allen, A., Teuben, P., Nemiroff, R.~J., and Shamir, L.\  2012,  "Practices 
in Code Discoverability: Astrophysics Source Code Library", Astronomical 
Data Analysis Software and Systems XXI,  {\bf 461} , 627- [{\bf 0 cit.}] 



% 100 INPROCEEDINGS  
\item  
Storm, S., and 7 colleagues.\  2013,  "Surveying the Dense Gas in Barnard 1 
and NGC 1333 from Cloud to Core Scales", Protostars and Planets VI Posters,  
, 1- [{\bf 0 cit.}] 

% 101 INPROCEEDINGS  
\item  
Teuben, P., Ip, C.~Y., Mundy, L., and Varshney, A.\  2013,  "Science 
Mining and Characterization of ALMA Large Data Cubes", Astronomical Data 
Analysis Software and Systems XXII,  {\bf 475} , 263- [{\bf 2 cit.}] 

% 102 INPROCEEDINGS  
\item  
Allen, A., and 10 colleagues.\  2013,  "Bring out your codes! Bring out 
your codes! (Increasing Software Visibility and Re-use)", Astronomical Data 
Analysis Software and Systems XXII,  {\bf 475} , 383- [{\bf 6 cit.}] 

% 103 INPROCEEDINGS  
\item  
Allen, A., and 5 colleagues.\  2013,  "Astrophysics Source Code Library", 
Astronomical Data Analysis Software and Systems XXII,  {\bf 475} , 387- 
[{\bf 3 cit.}] 

% 104 ARTICLE  
\item  
Allen, A., and 10 colleagues.\  2013,  "The Astrophysics Source Code 
Library: Where do we go from here?", ArXiv e-prints,  , arXiv:1312.5334- 
[{\bf 0 cit.}] 

% 105 ARTICLE  
\item  
DuPrie, K., and 10 colleagues.\  2013,  "Astrophysics Source Code Library: 
Incite to Cite!", ArXiv e-prints,  , arXiv:1312.6693- [{\bf 0 cit.}] 


% 112 INPROCEEDINGS  
\item  
Teuben, P., and 10 colleagues.\  2014,  "Ideas for Advancing Code Sharing: 
A Different Kind of Hack Day", Astronomical Data Analysis Software and 
Systems XXIII,  {\bf 485} , 3- [{\bf 0 cit.}] 

% 113 INPROCEEDINGS  
\item  
Teuben, P., Pound, M., Mundy, L., Looney, L., and Friedel, D.~N.\  2014,  
"The ALMA Data Mining Toolkit I: Archive Setup and User Usage", 
Astronomical Data Analysis Software and Systems XXIII,  {\bf 485} , 147- 
[{\bf 2 cit.}] 

% 114 INPROCEEDINGS  
\item  
Friedel, D.~N., Looney, L., Mundy, L., Pound, M., and Teuben, P.\  2014,  
"The ALMA Data Mining Toolkit II: Using ADMIT on Data Mined from the ALMA 
Archive", Astronomical Data Analysis Software and Systems XXIII,  {\bf 485} 
, 151- [{\bf 2 cit.}] 

% 115 INPROCEEDINGS  
\item  
DuPrie, K., and 10 colleagues.\  2014,  "Astrophysics Source Code Library: 
Incite to Cite!", Astronomical Data Analysis Software and Systems XXIII,  
{\bf 485} , 473- [{\bf 1 cit.}] 

% 116 INPROCEEDINGS  
\item  
Allen, A., and 10 colleagues.\  2014,  "The Astrophysics Source Code 
Library: Where Do We Go from Here?", Astronomical Data Analysis Software 
and Systems XXIII,  {\bf 485} , 477- [{\bf 2 cit.}] 

% 117 ARTICLE  
%\item  
%Zauderer, B.~A., and 21 colleagues.\  2014,  "The CARMA Paired Antenna 
%Calibration System: Atmospheric Phase Correction for Millimeter Wave 
%Interferometry and its Application to Mapping the Ultraluminous Galaxy Arp 
%193", ArXiv e-prints,  , arXiv:1410.5560- [{\bf 1 cit.}] 


% 121 ARTICLE  
\item  
Thomas, B., Shaya, E., Huang, Z., and Teuben, P.\  2015,  "Knowledge 
Discovery Framework for the Virtual Observatory", ArXiv e-prints,  , 
arXiv:1502.06501- [{\bf 0 cit.}] 


% 123 INPROCEEDINGS  
\item  
Friedel, D., and 7 colleagues.\  2015,  "Admit: Alma Data Mining Toolkit", 
70th International Symposium on Molecular Spectroscopy,  , \#WI15- [{\bf 0 
cit.}] 

% 124 INPROCEEDINGS  
\item  
Teuben, P., and 7 colleagues.\  2015,  "ADMIT: The ALMA Data Mining 
Toolkit", Astronomical Data Analysis Software an Systems XXIV (ADASS XXIV),  
{\bf 495} , 305- [{\bf 2 cit.}] 

% 125 INPROCEEDINGS  
\item  
Hanisch, R.~J., and 11 colleagues.\  2015,  "Astrophysics Source Code 
Library Enhancements", Astronomical Data Analysis Software an Systems XXIV 
(ADASS XXIV),  {\bf 495} , 453- [{\bf 0 cit.}] 

% 126 ARTICLE  
\item  
Allen, A., and 10 colleagues.\  2015,  "Improving Software Citation and 
Credit", ArXiv e-prints,  , arXiv:1512.07919- [{\bf 1 cit.}] 

% 127 INPROCEEDINGS  
\item  
Ginsburg, A., and 8 colleagues.\  2015,  "Radio Astronomy Tools in Python: 
Spectral-cube, pvextractor, and more", Revolution in Astronomy with ALMA: 
The Third Year,  {\bf 499} , 363-364.\  [{\bf 0 cit.}] 


% 130 INPROCEEDINGS  
\item  
Friedel, D., and 7 colleagues.\  2016,  "Alma Data Mining Toolkit", 71st 
International Symposium on Molecular Spectroscopy,  , \#RH12- [{\bf 0 
cit.}] 

% 131 INPROCEEDINGS  
\item  
Cox, E.~G., and 7 colleagues.\  2016,  "Filamentary Structure of Serpens 
Main and Serpens South Seen in N$_{2}$H$^{+}$, HCO$^{+}$, and HCN", 71st 
International Symposium on Molecular Spectroscopy,  , \#WH12- [{\bf 0 
cit.}] 

% 132 ARTICLE  
\item  
Allen, A., and 11 colleagues.\  2016,  "Astrophysics Source Code Library: 
Here we grow again!", ArXiv e-prints,  , arXiv:1611.06219- [{\bf 0 cit.}] 

% 133 ARTICLE  
\item  
Teuben, P., and 8 colleagues.\  2016,  "Implementing Ideas for Improving 
Software Citation and Credit", ArXiv e-prints,  , arXiv:1611.06232- [{\bf 1 
cit.}] 



% 136 ARTICLE  
\item  
Allen, A., and 5 colleagues.\  2017,  "Software metadata: How much is 
enough?", ArXiv e-prints,  , arXiv:1712.02398- [{\bf 0 cit.}] 

% 137 ARTICLE  
\item  
Allen, A., and 12 colleagues.\  2017,  "The Astrophysics Source Code 
Library: What's new, what's coming", ArXiv e-prints,  , arXiv:1712.02973- 
[{\bf 0 cit.}] 





% 144 ARTICLE  
\item  
Allen, A., Teuben, P.~J., and Ryan, P.~W.\  2018,  "Schoedinger's code: A 
preliminary study on research source code availability and link persistence 
in astrophysics", ArXiv e-prints,  , arXiv:1801.02094- [{\bf 0 cit.}] 

% 145 ARTICLE  
\item  
The Astropy Collaboration, and 136 colleagues.\  2018,  "The Astropy 
Project: Building an inclusive, open-science project and status of the v2.0 
core package", ArXiv e-prints,  , arXiv:1801.02634- [{\bf 0 cit.}] 

% 146 ARTICLE  
\item  
Dhabal, A., Mundy, L.~G., Rizzo, M.~J., Storm, S., and Teuben, P.\  2018,  
"Morphology and Kinematics of Filaments in the Serpens and Perseus 
Molecular Clouds", ArXiv e-prints,  , arXiv:1801.03155- [{\bf 0 cit.}] 


  

\end{enumerate}



%% II.D.3. Historical Conference Proceedings (10+ years ago)

%% II.D.4. Other





\underline{II.E. Conferences, Workshops, and Talks}

%% II.E.1. Keynotes

II.E.2. Invited Talks


\begin{enumerate}[resume,label=\textbf{\arabic*}.]  
\item
Invited talk and participant (E. van der Heuvel) to Stellar
Dynamics/N-body software workshop at U of Amsterdam (Jul 22-Aug 17,
1996 and Jan 19-23, 1998)

\item
Invited seminar and participant to the GH 2001 1-month workshop
``Disks of Galaxies:  Kinematics, Dynamics and Perturbations'',
Tonantzintla, Mexico (May 17-			31, 2001)

\item
Invited talk at Euro-VO DCA workshop, ESO/Munich (Apr 7-9, 2009)  

\item
Teuben, P.  1996,  "Gas and Shocks in Barred Galaxies",
IAU Colloq. 157: Barred Galaxies,  91,  299- [5 cit.]
** invited review, IAU 157, Alabama 1995 **

\item
Teuben, P., Regan, M., and Vogel, S.  1996,
"The Barred Galaxy NGC 1530", Lecture Notes in Physics, Berlin Springer Verlag,  474,  125- [0 cit.]
** invited talk Nobel Symposium, Stockholm 1995 **

\item
Teuben, Peter.  1998,  "Dynamical Modeling and Barred Galaxies",
Bulletin of the American Astronomical Society,  30,  1140- [0 cit.]
** invited talk at DDA, Charlottesville 1998 **

\item
Teuben, P. J.  2002,
"Velocity Fields of Disk Galaxies", Disks of Galaxies: Kinematics, Dynamics and Peturbations,  275,  217-228.  [8 cit.]
** invited talk, GH2001, Puebla, Mexico 2001 **

\item
Teuben, P.  2003,
"Simulation Software: Then, Now and Virtual Observatory",
Astrophysical Supercomputing using Particle Simulations,  208,  359- [1 cit.]
** invited talk, IAU 208, Tokyo, 2001
\end{enumerate}

II.E.3. Refereed Presentations


\begin{enumerate}[resume,label=\textbf{\arabic*}.]

% 75 TECHREPORT  
\item  
Lamb, J., and 9 colleagues.\  2009,  "Beating atmospheric scintillation at 
millimeter and submillimeter wavelengths", Society of Photo-Optical 
Instrumentation Engineers (SPIE) Conference Series,  ,  [{\bf 0 cit.}] 
  

% 94 INPROCEEDINGS  
\item  
Sivaramakrishnan, A., and 14 colleagues.\  2012,  "Non-redundant Aperture 
Masking Interferometry (AMI) and segment phasing with JWST-NIRISS", Space 
Telescopes and Instrumentation 2012: Optical, Infrared, and Millimeter 
Wave,  {\bf 8442} , 84422S- [{\bf 5 cit.}] 

\end{enumerate}

%% II.E.4. Refereed Abstracts

%% II.E.5. Refereed Posters

%% II.E.6. Refereed Panels

%% II.E.7. Non-Refereed Presentations

II.E.8. Non-Refereed Abstracts

% AAS poster and presentations

\begin{enumerate}[resume,label=\textbf{\arabic*}.]

% 4 INPROCEEDINGS  
\item  
Barnes, J., Hernquist, L.~E., Hut, P., and Teuben, P.\  1988,  "An 
Environment for Experiments in Stellar Dynamics", Bulletin of the American 
Astronomical Society,  {\bf 20} , 706- [{\bf 3 cit.}] 
% 7 INPROCEEDINGS  
\item  
Foster, S.~M.~and Teuben, P.\  1992,  "Early Dynamical Evolution of Open 
Clusters", Bulletin of the American Astronomical Society,  {\bf 24} , 
37.05- [{\bf 0 cit.}] 
% 8 INPROCEEDINGS  
\item  
Gruendl, R.~A., Vogel, S.~N., Teuben, P.~J., and Rand, R.~J.\  1992,  
"H{$\alpha$} Kinematic Observations of Spiral Density Waves in M51 with the 
Maryland-Caltech Fabry-Perot", Bulletin of the American Astronomical 
Society,  {\bf 24} , 40.12- [{\bf 0 cit.}] 
% 9 INPROCEEDINGS  
\item  
Spergel, D.~N., Blitz, L., and Teuben, P.\  1993,  "Distortions in the 
Galactic Disk", Bulletin of the American Astronomical Society,  {\bf 25} , 
60.04- [{\bf 0 cit.}] 

% 10 INPROCEEDINGS  
\item  
Piner, B.~G., Stone, J.~M., and Teuben, P.~J.\  1993,  "3-D Hydrodynamical 
Simulations of Gas Orbits in Barred Galaxies", Bulletin of the American 
Astronomical Society,  {\bf 25} , 76.05- [{\bf 1 cit.}] 
% 11 INPROCEEDINGS  
\item  
Teuben, P., Regan, M., Vogel, S., van der Hulst, T., and Wainscoat, R.\  
1993,  "The Giant Barred Spiral Galaxy NGC 1530", Bulletin of the American 
Astronomical Society,  {\bf 25} , 76.06- [{\bf 2 cit.}] 
% 19 INPROCEEDINGS  
\item  
Blitz, L., Spergel, D., Teuben, P., Hartmann, D., and Burton, W.~B.\  
1996,  "High Velocity Clouds: Remnants of Local Group Formation", Bulletin 
of the American Astronomical Society,  {\bf 28} , 61.01- [{\bf 5 cit.}] 

% 20 INPROCEEDINGS  
\item  
Spergel, D.~N., Blitz, L., Teuben, P.~J., Hartmann, D., and Burton, B.\  
1996,  "The Formation of the Local Group and the High Velocity Clouds", 
Bulletin of the American Astronomical Society,  {\bf 28} , 61.02- [{\bf 2 
cit.}] 
% 21 INPROCEEDINGS  
\item  
Barsony, M., Kenyon, S.~J., Lada, E.~A., and Teuben, P.~J.\  1996,  "A 
Near-Infrared Imaging Survey of the rho Ophiuchi Cloud Core", Bulletin of 
the American Astronomical Society,  {\bf 28} , 91.04- [{\bf 0 cit.}] 

% 22 INPROCEEDINGS  
\item  
Teuben, P.~and Wells, D.\  1997,  "FITS BoF Session", Astronomical Data 
Analysis Software and Systems VI,  {\bf 125} , 270- [{\bf 0 cit.}] 

% 23 INPROCEEDINGS  
\item  
Teuben, P.\  1997,  "Dynamic Dynamic Queries (DDQ)", Astronomical Data 
Analysis Software and Systems VI,  {\bf 125} , 329- [{\bf 0 cit.}]

% 29 INPROCEEDINGS  
\item  
Teuben, P.\  1998,  "Dynamical Modeling and Barred Galaxies", Bulletin of 
the American Astronomical Society,  {\bf 30} , 01.06- [{\bf 0 cit.}]

% 38 INPROCEEDINGS  
\item  
Regan, M.~W., Sheth, K., Vogel, S.~N., and Teuben, P.~J.\  2000,  "Inner 
Molecular Rings in Barred Galaxies: BIMA SONG Detections", Bulletin of the 
American Astronomical Society,  {\bf 32} , 58.01- [{\bf 0 cit.}] 

% 41 INPROCEEDINGS  
\item  
Fraga-Encinas, R., and 8 colleagues.\  2001,  "Rotation Curves of Nearby 
Spiral Galaxies", Bulletin of the American Astronomical Society,  {\bf 33} 
, 52.07- [{\bf 0 cit.}] 

% 42 INPROCEEDINGS  
\item  
Das, M., and 7 colleagues.\  2001,  "Bar Ellipticity and Central Mass 
Concentrations in Nearby Spiral Galaxies", Bulletin of the American 
Astronomical Society,  {\bf 33} , 58.12- [{\bf 5 cit.}] 

% 43 INPROCEEDINGS  
\item  
Regan, M.~W.~and Teuben, P.~J.\  2001,  "The Formation Mechanism of 
Nuclear Rings", Bulletin of the American Astronomical Society,  {\bf 33} , 
72.09- [{\bf 0 cit.}] 
% 44 INPROCEEDINGS  
\item  
Teuben, P.~J., Helfer, T., Vogel, S.~N., Wong, T., and Sheth, K.\  2001,  
"Simulations of Velocity Fields of Disk Galaxies", Bulletin of the American 
Astronomical Society,  {\bf 34} , 160.06- [{\bf 0 cit.}] 
% 46 INPROCEEDINGS  
\item  
Das, M., McGaugh, S.~S., Vogel, S.~N., Teuben, P.~J., and Kim, J.~H.\  
2002,  "CO Detections in Low Surface Brightness Galaxies using the BIMA 
Array", Bulletin of the American Astronomical Society,  {\bf 34} , 14.24- 
[{\bf 0 cit.}] 

% 47 INPROCEEDINGS  
\item  
Regan, M.~W.~and Teuben, P.~J.\  2002,  "Why Barred Galaxies do not have 
Inner Linblad Resonances", Bulletin of the American Astronomical Society,  
{\bf 34} , 26.01- [{\bf 0 cit.}] 

% 48 INPROCEEDINGS  
\item  
Staguhn, J.~G., Eckart, A., Schinnerer, E., and Teuben, P.~J.\  2002,  
"Interferometric Observations of Molecular Clouds in the Host Galaxy of the 
QSO I Zw 1", Bulletin of the American Astronomical Society,  {\bf 34} , 
112.05- [{\bf 0 cit.}] 
% 58 INPROCEEDINGS  
\item  
Das, M., Petitpas, G., Teuben, P.~J., and Vogel, S.~N.\  2003,  "Halo and 
Stellar Disk Masses in the Centers of Barred Spiral Galaxies", Bulletin of 
the American Astronomical Society,  {\bf 35} , 14.07- [{\bf 0 cit.}] 

% 59 INPROCEEDINGS  
\item  
Regan, M.~W.~and Teuben, P.~J.\  2003,  "How bar characteristics affect 
mass inflow", Bulletin of the American Astronomical Society,  {\bf 35} , 
65.03- [{\bf 0 cit.}] 

% 60 INPROCEEDINGS  
\item  
Teuben, P.~J.~and Pound, M.~W.\  2003,  "Teaching our (graduate) students 
how to AstroCompute ?", Bulletin of the American Astronomical Society,  
{\bf 35} , 135.09- [{\bf 0 cit.}] 
% 68 INPROCEEDINGS  
\item  
Thomas, B., Shaya, E., Huang, Z., and Teuben, P.\  2005,  "Knowledge 
Discovery Framework for the Virtual Observatory", Bulletin of the American 
Astronomical Society,  {\bf 37} , 25.01- [{\bf 0 cit.}] 

% 69 INPROCEEDINGS  
\item  
Shaya, E., Thomas, B., Teuben, P., and Huang, Z.\  2005,  "A Science 
Ontology for Goal Driven Datamining in Astronomy", Bulletin of the American 
Astronomical Society,  {\bf 37} , 29.14- [{\bf 0 cit.}] 

% 70 INPROCEEDINGS  
\item  
Shaya, E.~J., Thomas, B., Huang, Z., and Teuben, P.\  2007,  "OWLViper: 
Semantic Based Application for High Level Query and Analysis", American 
Astronomical Society Meeting Abstracts \#209,  {\bf 209} , 257.01- [{\bf 0 
cit.}] 
% 86 INPROCEEDINGS  
\item  
Allen, A., Nemiroff, R.~J., Shamir, L., and Teuben, P.~J.\  2012,  "The 
Astrophysics Source Code Library: An Update", American Astronomical Society 
Meeting Abstracts \#219,  {\bf 219} , 145.10- [{\bf 0 cit.}] 

% 87 INPROCEEDINGS  
\item  
McGaugh, S.~S., Katz, H., Teuben, P., and Angus, G.\  2012,  "The Masses 
and Bulk Velocities of Galaxy Clusters in Simulations of Structure 
Formation with QMOND", American Astronomical Society Meeting Abstracts 
\#220,  {\bf 220} , 435.03- [{\bf 0 cit.}] 
% 95 INPROCEEDINGS  
\item  
Allen, A., and 8 colleagues.\  2013,  "Using the Astrophysics Source Code 
Library", American Astronomical Society Meeting Abstracts \#221,  {\bf 221} 
, 240.01- [{\bf 0 cit.}] 

% 96 INPROCEEDINGS  
\item  
Teuben, P.~J., and 8 colleagues.\  2013,  "The MIS Pipeline Toolkit", 
American Astronomical Society Meeting Abstracts \#221,  {\bf 221} , 240.09- 
[{\bf 1 cit.}] 
% 97 INPROCEEDINGS  
\item  
Storm, S., and 24 colleagues.\  2013,  "CARMA Large Area Star-formation 
Survey: First Look at Barnard 1", American Astronomical Society Meeting 
Abstracts \#221,  {\bf 221} , 251.10- [{\bf 0 cit.}] 

% 98 INPROCEEDINGS  
\item  
Looney, L., and 24 colleagues.\  2013,  "CARMA Large Area Star-formation 
Survey: First Look at Serpens Main", American Astronomical Society Meeting 
Abstracts \#221,  {\bf 221} , 251.11- [{\bf 0 cit.}] 

% 99 INPROCEEDINGS  
\item  
Mundy, L.~G., and 24 colleagues.\  2013,  "CARMA Large-Area Star-formation 
Survey: First Look at NGC 1333 SVS-13 Region", American Astronomical 
Society Meeting Abstracts \#221,  {\bf 221} , 251.12- [{\bf 0 cit.}] % 106 INPROCEEDINGS  
\item  
Lee, K., and 12 colleagues.\  2014,  "Kinematics and Temperature Structures 
of Filaments in Serpens Main and Serpens South", American Astronomical 
Society Meeting Abstracts \#223,  {\bf 223} , 214.05- [{\bf 0 cit.}] 

% 107 INPROCEEDINGS  
\item  
Storm, S., and 11 colleagues.\  2014,  "Dendrogram Analysis of Large-Area 
CARMA Images in Perseus: the Dense Gas in NGC 1333, Barnard 1, and L1451", 
American Astronomical Society Meeting Abstracts \#223,  {\bf 223} , 214.06- 
[{\bf 0 cit.}]


% 108 INPROCEEDINGS  
\item  
Mundy, L.~G., and 11 colleagues.\  2014,  "The Structure of Dense Gas in 
Perseus and Serpens: CLASSy Results", American Astronomical Society Meeting 
Abstracts \#223,  {\bf 223} , 244.11- [{\bf 0 cit.}] 

% 109 INPROCEEDINGS  
\item  
Looney, L., and 13 colleagues.\  2014,  "Analysis of the Serpens South 
Filamentary Cloud: CLASSy Results", American Astronomical Society Meeting 
Abstracts \#223,  {\bf 223} , 244.12- [{\bf 0 cit.}] 

% 110 INPROCEEDINGS  
\item  
Teuben, P.~J., and 5 colleagues.\  2014,  "Software Reproduceability for 
Science Data", American Astronomical Society Meeting Abstracts \#223,  {\bf 
223} , 255.06- [{\bf 0 cit.}] 
% 111 INPROCEEDINGS  
\item  
Allen, A., and 11 colleagues.\  2014,  "You've Written a Cool Astronomy 
Code! Now What Do You Do with It?", American Astronomical Society Meeting 
Abstracts \#223,  {\bf 223} , 255.25- [{\bf 0 cit.}]

% 118 INPROCEEDINGS  
\item  
Sheth, K., and 8 colleagues.\  2015,  "ALMA and HST Observations of the 
Molecular Environment, Star formation Activity and Cluster Dissolution In 
NGC 1097", American Astronomical Society Meeting Abstracts,  {\bf 225} , 
227.05- [{\bf 0 cit.}] 

% 119 INPROCEEDINGS  
\item  
Friedel, D.~N., and 7 colleagues.\  2015,  "ADMIT: ALMA Data Mining 
Toolkit", American Astronomical Society Meeting Abstracts,  {\bf 225} , 
336.35- [{\bf 1 cit.}] 

% 120 INPROCEEDINGS  
\item  
Allen, A., and 11 colleagues.\  2015,  "Astrophysics Source Code Library -- 
Now even better!", American Astronomical Society Meeting Abstracts,  {\bf 
225} , 336.57- [{\bf 0 cit.}] 
% 128 INPROCEEDINGS  
\item  
Dhabal, A., and 6 colleagues.\  2016,  "Kinematics of Filaments in Serpens 
and Perseus", American Astronomical Society Meeting Abstracts,  {\bf 227} , 
347.09- [{\bf 0 cit.}] 

% 129 INPROCEEDINGS  
\item  
Allen, A., and 11 colleagues.\  2016,  "Making your code citable with the 
Astrophysics Source Code Library", American Astronomical Society Meeting 
Abstracts,  {\bf 227} , 348.01- [{\bf 0 cit.}] 
% 134 INPROCEEDINGS  
\item  
Allen, A., and 11 colleagues.\  2017,  "Top ten reasons to register your 
code with the Astrophysics Source Code Library", American Astronomical 
Society Meeting Abstracts,  {\bf 229} , 236.13- [{\bf 0 cit.}] 
% 138 INPROCEEDINGS  
\item  
Levy, R., and 11 colleagues.\  2018,  "The EDGE-CALIFA Survey: 
Molecular and Ionized Gas Kinematics in Nearby Galaxies", American 
Astronomical Society Meeting Abstracts \#231,  {\bf 231} , \#130.01- [{\bf 
0 cit.}] 

% 139 INPROCEEDINGS  
\item  
Allen, A., and 11 colleagues.\  2018,  "The Astrophysics Source Code 
Library by the numbers", American Astronomical Society Meeting Abstracts 
\#231,  {\bf 231} , \#150.10- [{\bf 0 cit.}] 
% 140 INPROCEEDINGS  
\item  
Teuben, P.~and Koda, J.\  2018,  "Combining Single Dish and 
Interferometric data: a new tool in CASA", American Astronomical Society 
Meeting Abstracts \#231,  {\bf 231} , \#150.17- [{\bf 0 cit.}] 

% 141 INPROCEEDINGS  
\item  
Ryan, P., Allen, A., and Teuben, P.\  2018,  "Schroedinger{\rsquo}s code: 
Source code availability and transparency in astrophysics", American 
Astronomical Society Meeting Abstracts \#231,  {\bf 231} , \#150.28- [{\bf 
0 cit.}] 

% 142 INPROCEEDINGS  
\item  
Allen, A.~and Teuben, P.\  2018,  "The Astrophysics Source Code Library: 
Supporting software publication and citation", American Astronomical 
Society Meeting Abstracts \#231,  {\bf 231} , \#307.10- [{\bf 0 cit.}]

% 143 INPROCEEDINGS  
\item  
Dhabal, A., and 5 colleagues.\  2018,  "Morphology and kinematics of 
filaments in Serpens and Perseus molecular clouds: a high resolution 
study", American Astronomical Society Meeting Abstracts \#231,  {\bf 231} , 
\#331.05- [{\bf 0 cit.}] 

  
\end{enumerate}

%% II.E.9. Non-Refereed Posters

% ALMA poster at UMUC, w/ Rob Swaters

%% II.E.10. Non-Refereed Panels

%% II.E.11. Symposia

II.E.12. Workshops

Averaging 1-2/yr over the past 5 years.

II.E.13. Colloquia

Averaging 1/yr over the past 5 years.

%% II.E.14. Historical Conferences, Workshops, Talks (10+ years ago)

II.E.15. Other

\begin{enumerate}[resume,label=\textbf{\arabic*}.]

% 11 ARTICLE   PJT-MOVE
\item  
Blitz, L.~and Teuben, P.\  1995,  "Symposium 169: Unresolved Problems of 
the Milky Way", Comments on Astrophysics,  {\bf 18} , 51- [{\bf 0 cit.}] 

% 14 INPROCEEDINGS   PJT-MOVE
\item  
Teuben, P., Regan, M., and Vogel, S.\  1996,  "The Barred Galaxy NGC 
1530", Lecture Notes in Physics, Berlin Springer Verlag,  {\bf 474} , 125- 
[{\bf 0 cit.}] 

% 43 ARTICLE   PJT-MOVE
\item  
Portegies Zwart, S., and 21 colleagues.\  2008,  "A Multiphysics and 
Multiscale Software Environment for Modeling Astrophysical Systems", 
Lecture Notes in Computer Science,  {\bf 5102} , 207-216.  [{\bf 2 cit.}] 

% 63 ARTICLE   PJT-MOVE
\item  
Bogert, F.~A., and 14 colleagues.\  2014,  "Computing in Astronomy: 
Applications and Examples", Computing,  {\bf 47} , 62-69.  [{\bf 0 cit.}] 


\end{enumerate}

\underline{II.F. Professional Publications}

II.F.1. Reports and Non-Refereed Monographs


\begin{enumerate}[resume,label=\textbf{\arabic*}.]  
\item
BIMA memo \#11: A. Rudolph and P. Teuben,
``Tests of Sparc and Disk Performance on Standard MIRIAD Tasks''. 1991.

\item
BIMA memo \#56: Jonathan Williams, and Peter Teuben,
``A MIRIAD routine for analyzing structures in Spectral Line Data Cubes'', 1997.

\item
BIMA memo \#81: P.J. Teuben,
``MIRIAD Benchmarks. I. Linux-Pentium and Solaris-Sparcs''. 2000.

\item
BIMA memo \#95: M.C.H. Wright and Peter Teuben ,
``Evaluation of the MIRIAD Package for ALMA Off-line Data Processing''. 2003.

\item
CARMA memo \#45:  Lisa Wei, Dave Woody, Peter Teuben, Misty La Vigne, and Stuart Vogel,
``Bandpass Calibration for CARMA'', 2008.

\item
CARMA memo \#51: Peter J. Teuben, B. Ashley Zauderer,
``Shadowing in the CARMA E-Array``, 2009.
\end{enumerate}
               
%% II.F.2. Pre-Print/Working Paper (Not Work in Progress)

%% II.F.3. Legal Briefs

%% II.F.4. Policy Briefs

%% II.F.5. Other


\underline{II.G. Book Reviews, Notes, and Other Contributions}

II.G. 1. Book Reviews

\begin{enumerate}[resume,label=\textbf{\arabic*}.]

% 24 ARTICLE  
\item  
 1997,  "Book Review: Unsolved problems of the Milky Way (IAU symp. 169) / 
Kluwer, 1996", The Observatory,  {\bf 117} , 109- [{\bf 1 cit.}] 

\end{enumerate}


%% II.G. 2. Essays

%% II.G. 3. Notes

II.G. 4. Manuals

NEMO Users and Programmers Guide (1987-)\newi
MIRIAD CARMA Cookbook (2007-2014)\newi
MIRIAD users guide\newi
MIRIAD programmers guide\newi
ManyBody Users Guide (2004-)\newi
BIMA Checker Guide (1996-2003)\newi


II.G. 5.Other


\underline{II.H. Completed Creative Works}


%% II.H.1. Digital Media (e.g., CDs, DVDs)

II.H.2. Datasets

\begin{enumerate}[resume,label=\textbf{\arabic*}.]
% 37 ARTICLE  
\item  
Phookun, B., Mundy, L., Teuben, P., and Wainscoat, R.\  2000,  "NGC 
4027-4027A: A lopsided spiral interacting with its satellite", Astronomy 
Data Image Library,  ,  [{\bf 0 cit.}] 

% 28 ARTICLE  
\item  
Barsony, M., Kenyon, S.~J., Lada, E.~A., and Teuben, P.~J.\  1998,  
"VizieR Online Data Catalog: Rho Oph Near-IR Positions and Photometry 
(Barsony+, 1997)", VizieR Online Data Catalog,  {\bf 211} ,  [{\bf 1 cit.}] 


% 135 ARTICLE  
\item  
Storm, S., and 20 colleagues.\  2017,  "VizieR Online Data Catalog: CLASSy: 
CARMA obs. in L1451 region of Perseus (Storm+, 2016)", VizieR Online Data 
Catalog,  {\bf 183} ,  [{\bf 0 cit.}] 
\end{enumerate}

%% II.H.3. Constructed Projects

II.H.4. Demonstrations

Visualization at AMNH, collaboration with NCSA, resulting in the
partiview program and a Users Guide as well as defining datasets that
have now become public via the Digital Universe (2001-2003)

``Theory in the Virtual Observatory'' demo at AAS  Atlanta, January 2004
                
%% II.H.5. Inventions

%% II.H.6. Original Plans and Designs

II.H.7. Photography

Various conference photography projects (Vera Rubin 81, Miller Goss
70, Martin Schwarzschild 100, van Woerden 90, many ADASS 2004-)

II.H.8. Software and Applications

Contributions (major and minor) to various software packages: NEMO,
MIRIAD, BIMA checker, WASP, AIPS++/CASA, ADMIT, CARMA, WIP, astromake,
tkrun, partiview, starlab, cmhog, athena, drpacs, manybody. A number of
them are now formally available for ASCL/ADS references:

\begin{enumerate}[resume,label=\textbf{\arabic*}.]


% 77 MISC  
\item  
Stone, J.~M., Gardiner, T.~A., Teuben, P., Hawley, J.~F., and Simon, 
J.~B.\  2010,  "Athena: Grid-based code for astrophysical 
magnetohydrodynamics (MHD)", Astrophysics Source Code Library,  , 
ascl:1010.014- [{\bf 1 cit.}]

% 78 MISC  
\item  
Barnes, J., Hut, P., and Teuben, P.\  2010,  "NEMO: A Stellar Dynamics 
Toolbox", Astrophysics Source Code Library,  , ascl:1010.051- [{\bf 2 
cit.}] 

% 79 MISC  
\item  
Piner, B.~G., Stone, J.~M., and Teuben, P.~J.\  2011,  "CMHOG: Code for 
Ideal Compressible Hydrodynamics", Astrophysics Source Code Library,  , 
ascl:1101.005- [{\bf 0 cit.}]

% 81 MISC  
\item  
Pound, M.~W., Wolfire, M.~G., Mundy, L.~G., Teuben, P., and Lord, S.\  
2011,  "DIRT: Dust InfraRed Toolbox", Astrophysics Source Code Library,  , 
ascl:1102.021- [{\bf 0 cit.}] 
% 83 MISC  
\item  
Sault, R.~J., Teuben, P., and Wright, M.~C.~H.\  2011,  "MIRIAD: 
Multi-channel Image Reconstruction, Image Analysis, and Display", 
Astrophysics Source Code Library,  , ascl:1106.007- [{\bf 9 cit.}] 
% 85 MISC  
\item  
Pound, M.~and Teuben, P.\  2011,  "MIS: A Miriad Interferometry Singledish 
Toolkit", Astrophysics Source Code Library,  , ascl:1110.025- [{\bf 0 
cit.}] 
% 90 MISC  
\item  
Kuzio de Naray, R., and 6 colleagues.\  2012,  "DiskFit: Modeling 
Asymmetries in Disk Galaxies", Astrophysics Source Code Library,  , 
ascl:1209.011- [{\bf 1 cit.}] 
% 122 MISC  
\item  
Hawley, J., Simon, J., Stone, J., Gardiner, T., and Teuben, P.\  2015,  
"Athena3D: Flux-conservative Godunov-type algorithm for compressible 
magnetohydrodynamics", Astrophysics Source Code Library,  , ascl:1505.006- 
[{\bf 0 cit.}] 


  
\end{enumerate}



II.H.9. Websites

Various websites/wikis for BIMA/CARMA/NEMO/MODEST/ManyBody

%% II.H.10. Exhibitions and Installations

%% II.H.11. Curatorial Practice

%% II.H.12. Performance or Interpretation --- Performing Arts

%% II.H.13. Direction - Performing Arts

%% II.H.14. Production - Performing Arts

%% II.H.15. Costume, Stage, Multimedia, and Theatrical Design

%% II.H.16. Artistic and Graphic Design

%% II.H.17. Dramaturgy

%% II.H.18. Artwork

%% II.H.19. Choreography

%% II.H.20. Playwriting, Screenwriting, and Musical Composition

%% II.H.21. Works of Creative Writing

%% II.H.22. Performance or Interpretation - Film, Video, and Multimedia

%% II.H.23. Direction - Film, Video, and Multimedia

%% II.H.24. Production - Film, Video, and Multimedia

%% II.H.25. Citations and Reviews

%% II.H.26. Historical Completed Creative Works (10+ years ago)

%% II.H.27. Other


%% \underline{II.I Significant Works in Public Media}

%% \textit{Specify the following --- Title, Publication/Media Name, Contributors, Types (Print, online, broadcast, video, documentary)}

%% II.I.1. Explanatory, Investigative, or Long-Form Journalism

%% II.I.2. Other Significant Journalism

%% II.I.3. Commentary/Analysis

%% II.I.4. Interactive Online Database

%% II.I.5. Other


\underline{II.J. Sponsored Research}

% \textit{List source, title, amount awarded, time period and role (i.e. principal investigator or co-investigator) in reverse chronological order or its inverse.  If there are co-investigators, please list these.}

II.J.1. Grants

Named PI: IAU/OAD (2016-2017) ``Haiti All Sky Camera''
		\$5,000

Named Co-I: w/ Jin Koda (2016-2017)
``Total Power Map to Visibilities (TP2VIS) -- Joint-Deconvolution of ALMA 12m, 7m \& Total Power Array Data''
		\$121,454

Named PI: NRAO (2018)
``ngVLA Short Spacing Issues for the Mapping of Nearby Galaxies'',
\$49,529

%% II.J.2. Contracts

%% II.J.3. Other


\underline{II.K. Fellowships, Gifts and Other Funded Research}


%% II.K.1. Fellowships

%% II.K.2. Gifts

II.K.3. Other

ESO Visiting Fellow (Nov-Dec 2017)



\underline{II.L. Submissions and Works in Progress}

% \textit{List press, journal, or granting agency.}

II.L.1. Current Grant Applications

Named PI: NASA ADAP, \$162,291
``Increasing the visibility of NASA astrophysics sofware through the ASCL''



%% II.L.2. Manuscripts in Preparation

%% II.L.3. Manuscripts under Review \textit{(indicate status:  submitted or revising to resubmit)}

%% II.L.4. Working Papers in Preparation

%% II.L.5. Designs in Preparation

%% II.L.6. Other


%% \underline{II.M. Centers for Research, Scholarship, and Creative Activities}

%% \textit{Specify Name of the Center, Description of Center, Collaborators, Start and End Dates.}

%% II.M.1. Centers Established

%% II.M.2. Centers Directed

%% II.M.3. Symposia Organized (through center)

%% II.M.4. Other


%% \underline{II.N. Patents}

%% II.N.1. Device

%% II.N.2. Other


\underline{II.O. Other Research/Scholarship/Creative Activities}


\textbf{III. Teaching, Mentoring and Advising.}


\underline{III.A. Courses Taught}

% \textit{Include courses taught in the last five years. Indicate approximate enrollments and any unusual formats.}

ASTR288P fall 2016 --  4 students -- mostly jupyter notebook teaching style, students laptops

ASTR288P spring 2017 -- 10 students -- mostly jupyter notebook teaching style, students laptops


\underline{III.B. Teaching Innovations}

%% III.B.1. Major Programs Established

%% III.B.2. Education Abroad Established
 
III.B.3. Software, Applications, Online Education, etc.

Jupyter notebooks for GradMap and ASTR288P

III.B.4. Instructional Workshops and Seminars Established

ManyBody - summerschool (20-40 students, 4 times, 2003-2010)\newi
CARMA summerschool (2007-2014) non-teaching contributions  1wk each, \ap 20 students each\newi
2009, 2016 PiTP Summerschool, Princeton (chairman: Scott Tremaine) - 2 wk, 110 students\newi
``Python and Astronomy'' - ESIH (Haiti) - 1 credit master class -  1wk, 26 students\newi
GradMap (2016-2017) - \ap 12 students

III.B.5. Course or Curriculum Development

ASTR288P\newi
For MODEST and GH: ``The ManyBody Guide''\newi
ASTR695ac - A series of computing oriented lectures for Graduate Students (Fall 2003, w/ Pound and others)\newi
GradMap \newi


%% III.B.6. Historical Innovations (10+ years ago)

%% III.B.7. Other


\underline{III.C. Advising}: Research or Clinical

% \textit{This refers to students whose projects the faculty has supervised as adviser, committee chair, or committee member (indicate role). The name of student, academic year(s) involved, and the name of institution if other than UMD should be indicated, as well as placement of the student(s), if the project is completed.  List completed work first.}

III.C.1. Undergraduate

\indent
1. Dave Coleman (Summer 1990) -- summer internship,programming tasks in MIRIAD\newi
2. Jeffrey Newman, Honors Thesis (1993/94) ``A Study of Bar Instabilities in Disk Galaxies: O\&P revisited''. Advisor: L. Blitz
3. Rotimi Osunsan (summer 1999) -- Java programming using Zoomable User Interfaces (jazz, w/ Katherine Plaisant, Ben Bederson, CS Dept)\newi
4. Vikas Shah (1999/2000) -- WASP Software Development w/ A.Harris - GRA mentor\newi
5. Misty La Vigne (Summer 2002) -- summer internship, w/ S. Vogel\newi
6. Pradeep Alankumaran (2007) -- w/ D. Richardson and MODEST group\newi
7. Brian Prager (Summer 2008) -- summer internship, extending tkrun to python\newi
8. Cathy Caviglia, B.S. (Astronomy), 2009,  ASTR498 ``Special Projects in Astronomy''.  Advisor:  S. McGaugh\newi
9. Harvey Katz, B.S. (Astronomy), 2012,  ASTR498  ``Special Projects inAstronomy''
 Advisor:  S. McGaugh -  this resulted in a refereed publication (52{\bf XX})\newi
10. Allan Benton (Summer 2016) -- McNair summer internship, warps in galaxies\newi
11. Thomas Coleman (Summer 2017) -- GradMap w/ A. Bolatto\newi

          
III.C.2. Master's


Robert Gruendl (1991 2nd year project) Advisor:  Vogel\newi
Scott Foster (1992 2nd year project) Advisor:  Vogel\newi
Jack Gallimore (1992, 2nd year project) Advisor:  Wilson\newi
Mike Regan (1992, 2nd year project) Advisor: Vogel\newi
Glenn Piner (1993 2nd year project) Advisor: Stone\newi
Kip Kuntz (1994, 2nd year project) Advisors:  Rand, Vogel\newi
Sven Geier (1995 2nd year project) Advisor: Bell\newi
Keith Watt (1995 2nd year projcet) Advisor:  Hamilton\newi
Kartik Sheth (1996, 2nd year project) Advisor:  Vogel\newi
James Marshall (1998 2nd year project) Advisor:  Ostriker\newi
Tim Robishaw (2000  2nd year project)  Advisor:  Vogel\newi
Rahul Shetty (2003  2nd year project) Advisor:  Vogel\newi
Misty LaVigne (2004 2nd year project) Advisor: Vogel\newi
Lisa Wei (2004 2nd year project) Advisor: Vogel\newi
Shaye Storm (2011 2nd year project) Advisor: Mundy\newi
Katherine Jameson  (2011 2nd year project) Advisor: Bolatto\newi
Rebecca Levy (2017 2nd year project)) Advisor:  Bolatto\newi
Arnab Dhabal (2017 2nd year project)) Advisor: Mundy\newi
                
III.C.3. Doctoral

Bikram Phookun , 1993. Advisor: Mundy\newi
Robert Gruendl, 1996. Advisor: Vogel\newi
Michael Regan, 1996, Advisor: Vogel\newi
Michelle Thornley, 1997, Advisor: Mundy\newi
Witold Maciejewski, 1997, Advisor: Sparke (U. Wisconsin)\newi
Kartik Sheth, 2001, Advisor: Vogel\newi
Rahul Shetty, 2007, Advisor: Vogel/Ostriker\newi
Misty La Vigne, 2009, Advisor: Vogel\newi
Lisa Wei, 2010, Advisor: Vogel\newi
Ashley Zauderer, 2010, Advisor: Vogel\newi
Shaye Storm, 2015, Advisor: Mundy\newi
Rodrigo Herrera Camus, 2015, Advisor: Bolatto\newi
Maxime Rizzo, 2016, Advisor: Mundy\newi
Katherine Jameson, 2016, Advisor: Bolatto\newi
                
III.C.4. Post-doctoral

% really?
% Musumi Das

III.C.5. Other Research Directions (K-12 Interactions)

ERHS internship - Amanda Keller (1996/97) - ``Dynamical Evolution of  Open Clusters''\newi
MBHS Summer internships: Ben Shaya (2008), Roger Curley (2009), Dalton Wu  (2009), all w/ M.Pound\newi

%% \underline{III.D. Mentorship}


%% III.D.1. Junior Faculty

%% III.D.2. Other


\underline{III.E. Advising: Other than Research Direction}


%% III.E.1. Undergraduate

%% III.E.2. Master's

%% III.E.3. Doctoral

%% III.E.4. Post-doctoral

III.E.5. Other Advising Activities

Faculty Advisor UM Linux Users Group [1995-]\newi
Faculty Advisor UM Badminton Club [1990-]\newi

% \textit{(Include advising student groups, special assignments, recruiting, etc.)}


\underline{III.F. Professional and Extension Education}

%% III.F.1. Professional Programs Established

%% III.F.2. Major Extension Programs

%% III.F.3. Workshops

III.F.4. Other

History Channel ``Season 4, Episode 7 (premiered Sep 29, 2009)'',
``The Search for Cosmic Clusters''. Interview + choreographed a 12-student gravity N-body problem



\underline{III.G. Other Teaching Activities}


\textbf{IV. Service and Outreach}


\underline{IV.A. Editorships, Editorial Boards, and Reviewing Activities}

%% \textit{Include participation for journals and other learned publications (print and electronic).}

%% IV.A.1. Editorships

%% IV.A.2. Editorial Boards

IV.A.3. Reviewing Activities for Journals and Presses

Referee of various journals (MNRAS, ApJ, PASP, A\&A, PASJ) averaging 2-3/yr over past 10 years.


IV.A.4. Reviewing Activities for Agencies and Foundations

Various NSF and NASA panels, averaging one every other year.

IV.A.5. Reviewing Activities for Conferences

% TODO-spell out
ADASS POC (2016-)

%% IV.A.6. Historical Editorships, etc. (10+ years ago)

%% IV.A.7. Other


\underline{IV.B. Committees, Professional \& Campus Service}

IV.B.1. Campus Service - Department

Computer Committee

IV.B.2. Campus Service - College

Maryland Day volunteer (about 10 times since its inception)\newi
SYSGROUP, a CMPS group meeting regularly discussing College computing issues\newi
Selection committee for astro. Dept. chair (2002)\newi

IV.B.3. Campus Service - University
                
National Capital Open  (badminton) Tournament Director, College Park (1992-2012)\newi
Host for Humphreys Fellow (2007-)\newi


%% IV.B.4. Campus Service - Special Administrative Assignment

%% IV.B.5. Campus Service - Other

%% IV.B.6. Offices and Committee Memberships 

IV.B.7. Leadership Roles in Meetings and Conferences

Astronomical Data Analysis Software and Systems (ADASS) 1994 (Baltimore), LOC member\newi
Guillermo Haro 2001 (Puebla, Mexico), SOC member\newi
Fast Multipole Method (FAM) 2004 (College Park), SOC member\newi
CARMA Science Symposium 2009, SOC member\newi
ADASS 2018 (Washington), LOC co-chair\newi
Future of Astronomical Data-analysis Systems (FADS) co-organizer at ADASS (1997-1999), w/ J. Noordam\newi
Various BoF sessions at ADASS (1994-2016)\newi      
ADASS POC (2016-)\newi

IV.B.8. Other Non-University Committees, Memberships, Panels, etc.

Chairman of the WGAS FITS Committee(1995-2001)\newi
FITS NOST1 panel (1991-1994) \newi
FITS NOST2 panel (1995-) -- this resulted in the Hanisch et.al (2001) paper\newi
Division of Dynamical Astronomy (AAS) Officer (2007-2009)\newi
IAU : member of commissions 5 \& 28\newi

%% IV.B.9. Historical Committees, etc. (10+ years ago)

IV.B.10. Other

CARMA Telescope Allocation Committee [2003?,2005, 2014]\newi
NASA review panel HPC [2006]\newi
NSF review panel  [2005, 2006]\newi
AAS abstract sorting [1991,2008]\newi


\underline{IV.C. External Service and Consulting}

IV.C.1. Community Engagements, Local, State, National, International

Thesis committee for Kimberly Engle (Drexel U., 1999, Advisor: S. McMillan)

Thesis committee for  A.C. Gonzalez-Garcia (U. Groningen, 2003, Advisor: T.S. van Albada) 

Thesis committee for Amr Hassan (Swinburne, Australia, 2012, Advisor: C. Fluke)

Thesis committee for Hector Noreiga-Mendoza (U Texas El Paso, advisor L. Aguilar; 2017)

Science Fair judge at Robert Goddard French Immersion (in French) [2003-2009]

GRAPHIT team member - a Jessup prison  education project using Open Source, w/ UMBC

HASC ``All Sky Camera in Haiti (2016-2018)''


%% IV.C.2. International Activities 

%% IV.C.3. Corporate and Other Board Memberships

%% IV.C.4. Entrepreneurial Activities

IV.C.5. Consultancies (to local, state and federal agencies; companies; organizations)

Consulting local company on a science education proposal for NSF (2007)\newi
Expert Witness on the illumination of light from the moon (2007)\newi
                
%% IV.C.6. Historical External Service and Consulting (10+ years ago)

%% IV.C.7. Other


%% \underline{IV.D. Non-Research Presentations}

%% IV.D.1. Outreach Presentations

%% IV.D.2 Other


%% \underline{IV.E. Media Contributions}

%% IV.E.1. Internet

%% IV.E.2. TV

%% IV.E.3. Radio

%% IV.E.4. Digital Media

%% IV.E.5. Print Media 

%% IV.E.6. Blogs

%% IV.E.7. Feeds

%% IV.E.8. Other


\underline{IV.F Community \& Other Service}


\textbf{V. Awards, Honors and Recognition}

%% V.1. Research Fellowships, Prizes and Awards

%% V.2 Teaching Awards

V.3 Service Awards and Honors

Distinguished Technical Professional Staff Prize (Astronomy Department, 2017)

%% V.4 Recognition in Media 

%% V.5 Other Special Recognition


\textbf{VI. Other Information}





\end{document}
